### 2019-03-21 paper.tex
Add in the beginning of the CVPR paper.

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr2019AuthorKit/latex/cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\begin{document}

%%%%%%%%% TITLE
\title{Multi-modal task transfer learning for Vehicle Re-Identification}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

Vehicle re-identification (re-id) aims at searching vehicle instances across nonoverlapping camera views by image matching. Influenced by the recent extensive studies on person re-id \cite{gong2014re}, vehicle re-id has started to gain increasing attention in the past two years, and a number of vehicle databases and additional labelling are now available to facilitate this research \cite{liu2016vehicleid,liu2016veri,yang2015large,kanaci2018vehicle,wang2017orientation}. This area promises the potential for more flexible means for vehicle recognition and search than Automatic Number Plate Recognition (ANPR). However, vehicle re-id by visual appearance is a
challenging task due to the very similar appearance of different vehicle instances
of the same model type and colour, and a significant visual appearance variation
of the same vehicle instance in different camera views \cite{}.

Due to the fact that vehicles are rigid objects, unlike people, the orientation of the vehicle can alter very predictably the appearance of in a particular viewpoint. Hence

In this paper we propose a new mutual learning based network architecture, that aims to simulataneously learn a number of tasks, an

\section{Multi-modal Vehicle Re-identification}

In order to perform Re-ID of previously unseen query vehicles, the aim of our model is to learn an feature embedding that allows for accurate retrivals based on distance (\eg L1) from the query image representation. In order to perform this task, we utilise training data containing a number of different labels: identity class labels, vehicle orientation class labels, and landmark position labels for a number of specific keypoints. We assume two sets of training examples $\mathcal{I_1} = \{\mathbf{I_i}\}_{i=1}^N$ and $\mathcal{I}_2 = \{\mathbf{I_i}\}_{i=1}^M$, containing $N$ and $M$ training images respectively. Both training sets contain the associated identity class labels $\mathcal{Y}_1=\{y_i\}_{i=1}^N$ and $\mathcal{Y}_2=\{y_i\}_{i=1}^M$, where $y_i \in \left[1,...,N_{id}\right]$ for $N_{id}$ distinct vehicle idenities spanning the two training sets. However, in addition, $\mathcal{I}_1$ also contains orientation and landmark position labels $\mathcal{O}=\{o_i\}_{i=1}^N$ $\mathcal{L}=\{\mathbf{l_i}\}_{i=1}^N$ respectively, where $o_i \in \left[1,...,N_O\right]$ is the orientation (for $N_O$ possible orientations), and  $\mathbf{l_i}=\{\left(x_{i,1},y_{i,1}\right),...,\left(x_{i,L},y_{i,L}\right)\}$ defines the position of $L$ keypoints, for the vehicle within image $\mathbf{I}_i$.

In order to perform accurate re-ID, we use this data to build a model constructed from a number of branches, each of which is tasked with learning a specific aspect of the data.

\subsection{Model Structure and Feature Learning}

\begin{figure*}
  \includegraphics[width=\linewidth,trim=0cm 10cm 0cm 0cm,clip=true]{images/system_overview.pdf}
  \label{F:overview}
  \caption{An overview of our proposed model (best viewed in colour). (A) Vehicle identity branch (B) Multi-scale analysis branch (C) Grayscale analysis branch (D) Vehicle orientation branch (E) Vehicle landmark localisation branch. Feedforward signals shown in black. Hard target (groundtruth) loss propogation shown in \textcolor{red}{red}. Soft target consensus feedback loss propogation shown in \textcolor{green}{green}.}
\end{figure*}

An overview of our proposed model can be seen in Figure \ref{F:overview}. The model is composed of a number of sub-branches, each of which is simultaneously learning a representation to solve its own set of tasks. In addition, there is a single fusion branch, which allows feature selection to be performed from the entire collection of individual representations.

Each sub-branch will now be described in more detail.

\paragraph{(A) Vehicle Identity}

The root branch of our model is tasked with learning the best representation for vehicle identity discrimination, for both training sets. Here, we exploit the cross entropy classification loss function in order to train one branch to predict vehicle identity. Thus the branch calculates the softmax posterior probability of the class label $y_i$ for a given training image $\mathbf{I_i}$:
\begin{equation}
  p_i^{ID} = p(\hat{y_i} = y_i|\mathbf{I_i}) = \frac{\exp(\hat{y_i})}{\sum_{k=1}^{N_{id}}\exp(\hat{y_k})}
  \label{E:softmax_id}
\end{equation}
where $\hat{y_k} = \mathbf{w_k^Tx_i}$, $\mathbf{x_i}$ is the feature vector for image $\mathbf{I_i}$ given by final layer of the branch, and $\mathbf{w_k}$ is the prediction function parameter for identity class $\emph{k}$. The loss across a minibatch of $N_B$ images can then be computed as:
\begin{equation}
  l_{ID} = -\frac{1}{N_B} \sum_{i=1}^{N_B} log(p_i^{ID})
  \label{E:cross_entropy_loss}
\end{equation}

\paragraph{(B) Multi-scale Analysis}

Here we exploit the multi-scale analysis that has previously been shown to be of benefit for the task of re-identification, both for persons \cite{chen2017person} and vehicles \cite{kanaci2018vehicle}. This is done by including a branch that is trained via cross entropy loss (Eq. \ref{E:cross_entropy_loss}) to predict the class identity from a rescaled version of the input image, in a similar way to branch A.

\paragraph{(C) Identity from Grayscale Image}

In order to force the model to focus on details of the vehicles, that allow for separation of highly similar identity classes, we ensure that one branch will be unable to use colour information for distinguishing between these classes. This is simply done by giving as input only the grayscale image, and again training the branch to predict identity via the cross entropy loss.

\paragraph{(D) Vehicle Orientation}

This branch is tasked with learning a representation to simultaneously predict the identity class and the orientation class, if known. In the case where the training images do not have associated orientation labels, this branch is trained in exactly the same way as the Vehicle Identity branch outlined above. However, when orientation labels are available, both sets of labels are simultaneously employed in a joint loss function in order to optimise the branch for prediction of both identity and orientation. Again, the cross entropy loss is employed for this task. Hence, the branch calculates both Eq. (\ref{E:softmax_id}), as well as the softmax posterior probability of the orientation label $o_i$ for the image:
\begin{equation}
  p_i^{O} = p(\hat{o_i} = o_i|\mathbf{I_i}) = \frac{\exp(\hat{o_i})}{\sum_{l=1}^{N_{O}}\exp(\hat{o_l})}
\end{equation}
where this time $\hat{o_l} = \mathbf{w_l^Tx_i}$, and $\mathbf{w_l}$ is the prediction function parameter for orientation class $\emph{l}$.

The loss for this branch across the minibatch of images can then be calculated as:
\begin{equation}
  l_{O} = -\frac{1}{N_B} \sum_{i=1}^{N_B}( log(p_i^{ID}) + log(p_i^{O}))
\end{equation}

\paragraph{(E) Vehicle Landmark Localisation}

Vehicle landmarks are distinguishing features that must be employed in order to perform correct  re-identification of vehicles that look very similar. Hence it is crucial that our model picks up on these in its feature representation. In order to attempt to ensure this, we task one branch with simultaneously predicting the position of these landmarks (if present) as well as the identity class. As above, if no landmark labels are available in the minibatch, this branch is trained in exactly the same way as branch A.

\paragraph{(F) Consensus Learning and Feedback}

In order to harness the benefit of all branches for the purpose of vehicle re-identification, we employ consensus learning as proposed in \cite{chen2017person} and previously harnessed for vehicle re-id in \cite{kanaci2018vehicle}. This is done via feature fusion of the final convolutional feature maps from all branches for consensus learning. As our branches are based on the MobileNet architecture, these feature maps are formed via an average pooling operation which result in feature vectors of length $1280$. Hence our fused features are of length $6400$. This is then passed to one additional identity softmax classification layer, again employed with cross entropy loss. Hence:
\begin{equation}
  p_i^C = p(\hat{y_i^C} = y_i|\mathbf{I_i}) = \frac{\exp(\hat{y_i^C})}{\sum_{k=1}^{N_{id}}\exp(\hat{y_k^C})}
\end{equation}

Additionally, we also utilise a consensus propogation mechanism, similar to the previously proposed method \cite{chen2017person,kanaci2018vehicle}. Here the consensus output is taken as 'soft targets' (as opposed to the groundtruth label 'hard targets') for the training data, and used to feedback information about the predictions made by the entire ensemble of branches. This is done concurrently with the training of the individual branches. Thie method is inspired by the idea of Knowledge Distillation (KD) \cite{hinton2015distilling}, but is different in that here we employ the combined predictions from all the 'student' branches as a \emph{virtual} teacher model, rather than utilising a pre-trainined powerful teacher model to provide the soft targets.

Specifically, the feedback mechanism employs the consensus probability predictions $P^C_i = \left[p_{i,1}^C,...,p_{i,j}^C,...,p_{i,N_{ID}}^C\right]$ given image $\mathbf{I_i}$, feeding these into the cross entropy loss between the two distributions to provide a consensus regularisation loss for the branch:
\begin{equation}
  \mathcal{H}_i = \mathcal{H}(P^C_i, P_i) = -\frac{1}{N_{ID}}\sum_{j=1}^{N_{ID}} p_j^c \log{p_j}
\end{equation}
The total consensus loss for a particular branch is then:
\begin{equation}
  l_{C} = \frac{1}{N_B} \sum_{i=1}^{N_B} \mathcal{H}_i
\end{equation}
This is added to each individual branches loss functions. In addition, this mechanism provides regularisation of the whole network by propogating all of the consensus losses back through the feature fusion layer, which also boosts the learning of the ensemble.

\subsection{Model Training}

\subsection{Vehicle Re-ID deployment}

\section{Experiments}

\section{Conclusions}

{\small
\bibliographystyle{cvpr2019AuthorKit/latex/ieee_fullname}
\bibliography{../Bibliography/reid_bibliography.bib}
}

\end{document}

### 2019-03-25 paper.tex
Add more details on the landmarks loss function.

@@
 Both training sets contain the associated identity class labels $\mathcal{Y}_1=\{y_i\}_{i=1}^N$ and $\mathcal{Y}_2=\{y_i\}_{i=1}^M$, where $y_i \in \left[1,...,N_{id}\right]$ for $N_{id}$ distinct vehicle idenities spanning the two training sets.
-However, in addition, $\mathcal{I}_1$ also contains orientation and landmark position labels $\mathcal{O}=\{o_i\}_{i=1}^N$ $\mathcal{L}=\{\mathbf{l_i}\}_{i=1}^N$ respectively, where $o_i \in \left[1,...,N_O\right]$ is the orientation (for $N_O$ possible orientations), and  $\mathbf{l_i}=\{\left(x_{i,1},y_{i,1}\right),...,\left(x_{i,L},y_{i,L}\right)\}$ defines the position of $L$ keypoints, for the vehicle within image $\mathbf{I}_i$.
+However, in addition, $\mathcal{I}_1$ also contains orientation and landmark position labels $\mathcal{O}=\{o_i\}_{i=1}^N$ $\mathcal{L}=\{\mathbf{l_i}\}_{i=1}^N$ respectively, where $o_i \in \left[1,...,N_O\right]$ is the orientation (for $N_O$ possible orientations), and  $\mathbf{l_i}=\{\left(x_{i,1},y_{i,1}\right),...,\left(x_{i,L},y_{i,L}\right)\}$ defines the position of $L$ keypoint landmarks for the vehicle within image $\mathbf{I}_i$, which we normalise according to the image size so that $x,y \in [0,1]$
 
@@
 (A) Vehicle identity branch (B) Multi-scale analysis branch (C) Grayscale analysis branch (D) Vehicle orientation branch (E) Vehicle landmark localisation branch.
+(F) Consensus learning through feature fusion.
 Feedforward signals shown in black.
@@
 In addition, there is a single fusion branch, which allows feature selection to be performed from the entire collection of individual representations.
-
+It is the output from this branch that is taken during deployment.
 Each sub-branch will now be described in more detail.
@@
 \begin{equation}
-  p_i^{O} = p(\hat{o_i} = o_i|\mathbf{I_i}) = \frac{\exp(\hat{o_i})}{\sum_{l=1}^{N_{O}}\exp(\hat{o_l})}
+  p_i^{O} = p(\hat{o_i} = o_i|\mathbf{I_i}) = \frac{\exp(\hat{o_i})}{\sum_{j=1}^{N_{O}}\exp(\hat{o_j})}
 \end{equation}
-where this time $\hat{o_l} = \mathbf{w_l^Tx_i}$, and $\mathbf{w_l}$ is the prediction function parameter for orientation class $\emph{l}$.
+where this time $\hat{o_j} = \mathbf{w_j^Tx_j}$, and $\mathbf{w_j}$ is the prediction function parameter for orientation class $\emph{j}$.
 
@@
 As above, if no landmark labels are available in the minibatch, this branch is trained in exactly the same way as branch A.
+
+If landmark groundtruth labels are available, these are employed to train the branch to predict the location of the landmarks which are present, while at the same time predict identity.
+As a different set of landmarks are visible, depending on the orientation of the vehicle, we need to take the absence of landmarks altogether into account when training this branch.
+Thus, we design a loss function that only penalises the predictions for landmarks that are present in the groundtruth labels for the minibatch examples.
+As this is the regression problem, we also set the final layer of the branch to output with linear activation, and take the Mean Squared Error (MSE) as the basis for our custom loss function.
+If the landmarks were all present in every training image, we could use the standard MSE loss:
+\begin{equation}
+  l_{LM} = \frac{1}{N_B} \sum_{j=1}^{N_L} \sum_{i=1}^{N_B} (\hat{x_{i,j}} - x_{i,j})^2 + (\hat{y_{i,j}} - y_{i,j})^2
+\end{equation}
+Where $\hat{x_{i,j}}$ and $\hat{y_{i,j}}$ are the predicted normalised coordinates.
+However, we need to alter this to remove landmarks that are not present at all in the image.
+Hence we design a selective MSE function that only takes into account those landmarks which the groundtruth labels indicate are present in the image.
+Thus:
+\begin{equation}
+  l_{LM} = \sum_{j=1}^{N_L} \frac{1}{N_{B_j}} \sum_{i \in B_j} (\hat{x_{i,j}} - x_{i,j})^2 + (\hat{y_{i,j}} - y_{i,j})^2 
+\end{equation}
+where $B_j$ is the subset of the minibatch examples for which landmark $j$ is present in image $\mathbf{I_i}$.
+Due to the nature of the landmarks, we expect that there will be a similar number of examples in the batch that contain each landmark, hence we can approximate this as:
+\begin{equation}
+  l_{LM} = \frac{1}{\bar{N_{B_j}}} \sum_{j=1}^{N_L}  \sum_{i \in B_j} (\hat{x_{i,j}} - x_{i,j})^2 + (\hat{y_{i,j}} - y_{i,j})^2 
+\end{equation}
+in order to simplify the calculation.
 

### 2019-03-26 paper.tex
Minor changes.

@@
 \begin{equation}
-  l_{ID} = -\frac{1}{N_B} \sum_{i=1}^{N_B} log(p_i^{ID})
+  l_{ID} = -\frac{1}{N_B} \sum_{i=1}^{N_B} \log{p_i^{ID}}
   \label{E:cross_entropy_loss}
@@
 \begin{equation}
-  l_{O} = -\frac{1}{N_B} \sum_{i=1}^{N_B}( log(p_i^{ID}) + log(p_i^{O}))
+  l_{O} = -\frac{1}{N_B} \sum_{i=1}^{N_B}(\log{p_i^{ID}} + \log{p_i^{O}})
 \end{equation}
@@
 \begin{equation}
-  l_{LM} = \frac{1}{N_B} \sum_{j=1}^{N_L} \sum_{i=1}^{N_B} (\hat{x_{i,j}} - x_{i,j})^2 + (\hat{y_{i,j}} - y_{i,j})^2
+  M = \frac{1}{N_B} \sum_{j=1}^{N_L} \sum_{i=1}^{N_B} (\hat{x_{i,j}} - x_{i,j})^2 + (\hat{y_{i,j}} - y_{i,j})^2
 \end{equation}
-Where $\hat{x_{i,j}}$ and $\hat{y_{i,j}}$ are the predicted normalised coordinates.
+where $\hat{x_{i,j}}$ and $\hat{y_{i,j}}$ are the predicted normalised coordinates.
 However, we need to alter this to remove landmarks that are not present at all in the image.
@@
 \begin{equation}
-  l_{LM} = \sum_{j=1}^{N_L} \frac{1}{N_{B_j}} \sum_{i \in B_j} (\hat{x_{i,j}} - x_{i,j})^2 + (\hat{y_{i,j}} - y_{i,j})^2 
+  M = \sum_{j=1}^{N_L} \frac{1}{N_{B_j}} \sum_{i \in B_j} (\hat{x_{i,j}} - x_{i,j})^2 + (\hat{y_{i,j}} - y_{i,j})^2 
 \end{equation}
 where $B_j$ is the subset of the minibatch examples for which landmark $j$ is present in image $\mathbf{I_i}$.
-Due to the nature of the landmarks, we expect that there will be a similar number of examples in the batch that contain each landmark, hence we can approximate this as:
+Due to the nature of the landmarks, we can assume that there will be a similar number of examples in the batch that contain each landmark, hence we can approximate this as:
 \begin{equation}
-  l_{LM} = \frac{1}{\bar{N_{B_j}}} \sum_{j=1}^{N_L}  \sum_{i \in B_j} (\hat{x_{i,j}} - x_{i,j})^2 + (\hat{y_{i,j}} - y_{i,j})^2 
+  M = \frac{1}{\bar{N_{B_j}}} \sum_{j=1}^{N_L}  \sum_{i \in B_j} (\hat{x_{i,j}} - x_{i,j})^2 + (\hat{y_{i,j}} - y_{i,j})^2 
 \end{equation}
-in order to simplify the calculation.
+where $\bar{N_{B_j}}$ is the mean number of examples containing each landmark, in order to simplify the calculation. Then the full loss function for the landmark branch becomes:
+\begin{equation}
+  l_{LM} = M - \frac{1}{N_B} \sum_{i=1}^{N_B} \log{p_i}
+\end{equation}
 

### 2019-04-02 paper.tex
Minor changes to the introductory description.

@@
 In order to perform this task, we utilise training data containing a number of different labels: identity class labels, vehicle orientation class labels, and landmark position labels for a number of specific keypoints.
-We assume two sets of training examples $\mathcal{I_1} = \{\mathbf{I_i}\}_{i=1}^N$ and $\mathcal{I}_2 = \{\mathbf{I_i}\}_{i=1}^M$, containing $N$ and $M$ training images respectively.
+We assume two sets of training examples $\mathcal{I}_1 = \{\mathbf{I_i}\}_{i=1}^N$ and $\mathcal{I}_2 = \{\mathbf{I_i}\}_{i=1}^M$, containing $N$ and $M$ training images respectively.
 Both training sets contain the associated identity class labels $\mathcal{Y}_1=\{y_i\}_{i=1}^N$ and $\mathcal{Y}_2=\{y_i\}_{i=1}^M$, where $y_i \in \left[1,...,N_{id}\right]$ for $N_{id}$ distinct vehicle idenities spanning the two training sets.
-However, in addition, $\mathcal{I}_1$ also contains orientation and landmark position labels $\mathcal{O}=\{o_i\}_{i=1}^N$ $\mathcal{L}=\{\mathbf{l_i}\}_{i=1}^N$ respectively, where $o_i \in \left[1,...,N_O\right]$ is the orientation (for $N_O$ possible orientations), and  $\mathbf{l_i}=\{\left(x_{i,1},y_{i,1}\right),...,\left(x_{i,L},y_{i,L}\right)\}$ defines the position of $L$ keypoint landmarks for the vehicle within image $\mathbf{I}_i$, which we normalise according to the image size so that $x,y \in [0,1]$
+However, in addition, $\mathcal{I}_1$ also contains orientation and landmark position labels $\mathcal{O}=\{o_i\}_{i=1}^N$ and $\mathcal{L}=\{\mathbf{l_i}\}_{i=1}^N$, where $o_i \in \left[1,...,N_O\right]$ is the orientation (for $N_O$ possible orientations), and  $\mathbf{l_i}=\{\left(x_{i,1},y_{i,1}\right),...,\left(x_{i,L},y_{i,L}\right)\}$ defines the position of $L$ keypoint landmarks for the vehicle within image $\mathbf{I}_i$, which we normalise according to the image size so that $x,y \in [0,1]$
 

### 2019-04-02 paper.tex
Add in algo train and test details.

@@
 \usepackage{xcolor}
+\usepackage{algorithm}
+\usepackage{algorithmic}
 
@@
 Both training sets contain the associated identity class labels $\mathcal{Y}_1=\{y_i\}_{i=1}^N$ and $\mathcal{Y}_2=\{y_i\}_{i=1}^M$, where $y_i \in \left[1,...,N_{id}\right]$ for $N_{id}$ distinct vehicle idenities spanning the two training sets.
-However, in addition, $\mathcal{I}_1$ also contains orientation and landmark position labels $\mathcal{O}=\{o_i\}_{i=1}^N$ and $\mathcal{L}=\{\mathbf{l_i}\}_{i=1}^N$, where $o_i \in \left[1,...,N_O\right]$ is the orientation (for $N_O$ possible orientations), and  $\mathbf{l_i}=\{\left(x_{i,1},y_{i,1}\right),...,\left(x_{i,L},y_{i,L}\right)\}$ defines the position of $L$ keypoint landmarks for the vehicle within image $\mathbf{I}_i$, which we normalise according to the image size so that $x,y \in [0,1]$
+However, in addition, $\mathcal{I}_1$ also contains orientation and landmark position labels $\mathcal{O}=\{o_i\}_{i=1}^N$ and $\mathcal{L}=\{\mathbf{l_i}\}_{i=1}^N$, where $o_i \in \left[1,...,N_O\right]$ is the orientation (for $N_O$ possible orientations), and  $\mathbf{l_i}=\{\left(x_{i,1},y_{i,1}\right),...,\left(x_{i,L},y_{i,L}\right)\}$ defines the position of $N_L$ keypoint landmarks for the vehicle within image $\mathbf{I}_i$, which we normalise according to the image size so that $x,y \in [0,1]$
 
@@
 Feedforward signals shown in black.
-Hard target (groundtruth) loss propogation shown in \textcolor{red}{red}.
-Soft target consensus feedback loss propogation shown in \textcolor{green}{green}.}
+Hard target (groundtruth) loss propagation shown in \textcolor{red}{red}.
+Soft target consensus feedback loss propagation shown in \textcolor{green}{green}.}
 \end{figure*}
@@
 
-Additionally, we also utilise a consensus propogation mechanism, similar to the previously proposed method \cite{chen2017person,kanaci2018vehicle}.
+Additionally, we also utilise a consensus propagation mechanism, similar to the previously proposed method \cite{chen2017person,kanaci2018vehicle}.
 Here the consensus output is taken as 'soft targets' (as opposed to the groundtruth label 'hard targets') for the training data, and used to feedback information about the predictions made by the entire ensemble of branches.
 This is done concurrently with the training of the individual branches.
-Thie method is inspired by the idea of Knowledge Distillation (KD) \cite{hinton2015distilling}, but is different in that here we employ the combined predictions from all the 'student' branches as a \emph{virtual} teacher model, rather than utilising a pre-trainined powerful teacher model to provide the soft targets.
+Thie method is inspired by the idea of Knowledge Distillation (KD) \cite{hinton2015distilling}, but is different in that here we employ the combined predictions from all the `student' branches as a \emph{virtual} teacher model, rather than utilising a pre-trainined powerful teacher model to provide the soft targets.
 
@@
 \end{equation}
-This is added to each individual branches loss functions.
-In addition, this mechanism provides regularisation of the whole network by propogating all of the consensus losses back through the feature fusion layer, which also boosts the learning of the ensemble.
+This is added to each individual branch's loss functions.
+In addition, this mechanism provides regularisation of the whole network by propagating all of the consensus losses back through the feature fusion layer, which also boosts the learning of the ensemble.
 
@@
 
+As we have two training sets, each of which contain different groundtruth labels, we adopt an alternate training schedule to optimise our model.
+We first train on our larger training set, which contains
+
+\begin{algorithm}[t]
+  \caption{The model training algorithm}
+  \label{A:model_training}
+  \begin{algorithmic}
+    \REQUIRE{Training sets $\mathcal{I}_1$ $\mathcal{I}_2$, labels $\mathcal{Y}_1$\
+      $\mathcal{O}$ $\mathcal{L}$ $\mathcal{Y}_2$, model $\mathcal{M}$}
+    \STATE{$\bullet$ Initialise network branches with pre-trained ImageNet weights}
+    \STATE{$\bullet$ Initialise output layers of $\mathcal{M}$ randomly}
+
+    \FOR{epoch $e \in (1, E)$}
+
+      \FOR{each training set $\mathcal{I} \in (\mathcal{I}_1,\mathcal{I}_2)$}
+        \STATE{$\bullet$ Feed-forward through model to obtain all branch identity classification \
+        predictions on images in $\mathcal{I}$}
+
+        \IF{$\mathcal{I}$ has associated $\mathcal{O}$ and $\mathcal{L}$}
+          \STATE{$\bullet$ Feed-forward to obtain orientation classification and landmark regression \
+        predictions}
+        \ENDIF
+
+        \STATE{$\bullet$ Fuse features and perform consensus identity classification predictions}
+        \STATE{$\bullet$ Calculate hard and soft losses for each branch and backpropagate to update weights}
+        \STATE{$\bullet$ Calculate hard and soft losses for the consensus branch and backpropagate}
+
+      \ENDFOR
+    \ENDFOR
+
+  \end{algorithmic}
+\end{algorithm}
+
 \subsection{Vehicle Re-ID deployment}
+
+During deployment, we employ the feature fusion layer from our trained model as the full feature representation in order to perform vehicle re-identification matching.
+As we do not necessarily have camera information about the query or gallery images, or timestamp information, which would allow the use of camera distance or time-based analysis, we use only a generic distance metric - the $L1$ metric - in order to match gallery images to the query.
+Hence, for each of the query image $\mathbf{I}^q$, and the gallery images $\{\mathbf{I}_i^g\}$,  we compute our $6400$ dimension fused feature representations, $\mathbf{x}^q$ and $\{\mathbf{x}_i^g\}$ respectively.
+We then calculate the $L1$ distance between the query representation and each of the gallery images, and rank the latter by increasing distance in order to calculate the Rank-1 and mAP performance scores.
 

### 2019-04-04 paper.tex
Minor changes.

@@
 %%%%%%%%% TITLE
-\title{Multi-modal task transfer learning for Vehicle Re-Identification}
+\title{Multi-task Mutual Learning for Vehicle Re-Identification}
 
@@
 
-Due to the fact that vehicles are rigid objects, unlike people, the orientation of the vehicle can alter very predictably the appearance of in a particular viewpoint. Hence
+Due to the fact that vehicles are rigid objects, unlike people, the orientation of the vehicle can alter very predictably the appearance of in a particular viewpoint.
+\emph{TODO motivation and related work}
 
-In this paper we propose a new mutual learning based network architecture, that aims to simulataneously learn a number of tasks, an
+In this paper we propose a new mutual learning based network architecture, that aims to simulataneously learn a number of tasks and then use consensus learning to build an improved representation for the purpose of vehicle re-identification.
 
@@
 
-In order to perform accurate re-ID, we use this data to build a model constructed from a number of branches, each of which is tasked with learning a specific aspect of the data.
+In order to perform accurate re-ID, we use this data to build a model constructed from a number of branches, each of which is tasked with learning a specific aspect of the data. \emph{TODO expand}
 
@@
 
-As we have two training sets, each of which contain different groundtruth labels, we adopt an alternate training schedule to optimise our model.
-We first train on our larger training set, which contains
+As we have two training sets, each of which contain different groundtruth labels, we adopt an alternate training schedule to optimise our model. \emph{TODO}
 

### 2019-04-24 paper.tex
change abstract

@@
 \begin{abstract}
-  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract
+
 \end{abstract}
@@
 \bibliographystyle{cvpr2019AuthorKit/latex/ieee_fullname}
-\bibliography{../Bibliography/reid_bibliography.bib}
+\bibliography{bibliography.bib}
 }

### 2019-04-25 paper.tex
Remove the landmarks branch, plus a few other minor updates. Start on experiment section.

@@
 \usepackage{algorithmic}
+\usepackage{multirow}
 
@@
 \begin{figure*}
-  \includegraphics[width=\linewidth,trim=0cm 10cm 0cm 0cm,clip=true]{images/system_overview.pdf}
+  \includegraphics[width=\linewidth,trim=0cm 8cm 0cm 0cm,clip=true]{images/system_overview_orient_only.pdf}
   \label{F:overview}
-  \caption{An overview of our proposed model (best viewed in colour).
-(A) Vehicle identity branch (B) Multi-scale analysis branch (C) Grayscale analysis branch (D) Vehicle orientation branch (E) Vehicle landmark localisation branch.
-(F) Consensus learning through feature fusion.
+  \caption{An overview of our proposed model (best viewed in colour). (A) Vehicle identity branch (B) Multi-scale analysis branch (C) Grayscale analysis branch (D) Vehicle orientation branch
+    %(E) Vehicle landmark localisation branch.
+(E) Consensus learning through feature fusion.
 Feedforward signals shown in black.
@@
 
-In order to force the model to focus on details of the vehicles, that allow for separation of highly similar identity classes, we ensure that one branch will be unable to use colour information for distinguishing between these classes.
+In order to encourage the model to focus on details of the vehicles, that allow for separation of highly similar identity classes, we ensure that one branch will be unable to use colour information for distinguishing between these classes.
 This is simply done by giving as input only the grayscale image, and again training the branch to predict identity via the cross entropy loss.
@@
 
-This branch is tasked with learning a representation to simultaneously predict the identity class and the orientation class, if known.
-In the case where the training images do not have associated orientation labels, this branch is trained in exactly the same way as the Vehicle Identity branch outlined above.
-However, when orientation labels are available, both sets of labels are simultaneously employed in a joint loss function in order to optimise the branch for prediction of both identity and orientation.
-Again, the cross entropy loss is employed for this task.
+This branch is tasked with learning a representation to simultaneously predict the identity class and the orientation class, for examples for which this is known.
+%In the case where the training images do not have associated orientation labels, this branch is trained in exactly the same way as the Vehicle Identity branch outlined above.
+Both sets of labels are simultaneously employed in a joint loss function in order to optimise the branch for prediction of both identity and orientation.
+As orientation labels are not available for all training data, we employ a selective classifcation subset loss function, that allows the loss to be calculated across only the subset of the batch for which orientation labels are known.
+
+Again, the cross entropy loss is exploited for this task.
 Hence, the branch calculates both Eq.
-(\ref{E:softmax_id}), as well as the softmax posterior probability of the orientation label $o_i$ for the image:
+(\ref{E:softmax_id}), as well as the softmax posterior probability of the orientation label $o_i$ for the images for which the orientation class is known:
 \begin{equation}
@@
 
-The loss for this branch across the minibatch of images can then be calculated as:
+The loss for this branch is then calculated across the minibatch of images as:
 \begin{equation}
-  l_{O} = -\frac{1}{N_B} \sum_{i=1}^{N_B}(\log{p_i^{ID}} + \log{p_i^{O}})
+  l_{O} = -\frac{1}{N_B} \sum_{i=1}^{N_B}\log{p_i^{ID}} + \frac{1}{N_S} \sum_{i=1}^{N_B}q_i^O
 \end{equation}
+where $N_S$ is the size of the subset of the minibatch for which orientation labels are known, and
+\[
+q_i^O =
+\begin{cases}
+    \log{p_i^{O}} & \text{if } o_i \in \mathcal{O} \\
+    0 & \text{otherwise}
+\end{cases}
+\]
+%% \paragraph{(E) Vehicle Landmark Localisation}
 
-\paragraph{(E) Vehicle Landmark Localisation}
-
-Vehicle landmarks are distinguishing features that must be employed in order to perform correct  re-identification of vehicles that look very similar.
+%% Vehicle landmarks are distinguishing features that must be employed in order to perform correct  re-identification of vehicles that look very similar.
 Hence it is crucial that our model picks up on these in its feature representation.
@@
 
-If landmark groundtruth labels are available, these are employed to train the branch to predict the location of the landmarks which are present, while at the same time predict identity.
+%% If landmark groundtruth labels are available, these are employed to train the branch to predict the location of the landmarks which are present, while at the same time predict identity.
 As a different set of landmarks are visible, depending on the orientation of the vehicle, we need to take the absence of landmarks altogether into account when training this branch.
@@
 If the landmarks were all present in every training image, we could use the standard MSE loss:
-\begin{equation}
-  M = \frac{1}{N_B} \sum_{j=1}^{N_L} \sum_{i=1}^{N_B} (\hat{x_{i,j}} - x_{i,j})^2 + (\hat{y_{i,j}} - y_{i,j})^2
-\end{equation}
-where $\hat{x_{i,j}}$ and $\hat{y_{i,j}}$ are the predicted normalised coordinates.
+%% \begin{equation}
+%%   M = \frac{1}{N_B} \sum_{j=1}^{N_L} \sum_{i=1}^{N_B} (\hat{x_{i,j}} - x_{i,j})^2 + (\hat{y_{i,j}} - y_{i,j})^2
+%% \end{equation}
+%% where $\hat{x_{i,j}}$ and $\hat{y_{i,j}}$ are the predicted normalised coordinates.
 However, we need to alter this to remove landmarks that are not present at all in the image.
@@
 Thus:
-\begin{equation}
-  M = \sum_{j=1}^{N_L} \frac{1}{N_{B_j}} \sum_{i \in B_j} (\hat{x_{i,j}} - x_{i,j})^2 + (\hat{y_{i,j}} - y_{i,j})^2
-\end{equation}
-where $B_j$ is the subset of the minibatch examples for which landmark $j$ is present in image $\mathbf{I_i}$.
+%% \begin{equation}
+%%   M = \sum_{j=1}^{N_L} \frac{1}{N_{B_j}} \sum_{i \in B_j} (\hat{x_{i,j}} - x_{i,j})^2 + (\hat{y_{i,j}} - y_{i,j})^2
+%% \end{equation}
+%% where $B_j$ is the subset of the minibatch examples for which landmark $j$ is present in image $\mathbf{I_i}$.
 Due to the nature of the landmarks, we can assume that there will be a similar number of examples in the batch that contain each landmark, hence we can approximate this as:
-\begin{equation}
-  M = \frac{1}{\bar{N_{B_j}}} \sum_{j=1}^{N_L}  \sum_{i \in B_j} (\hat{x_{i,j}} - x_{i,j})^2 + (\hat{y_{i,j}} - y_{i,j})^2
-\end{equation}
-where $\bar{N_{B_j}}$ is the mean number of examples containing each landmark, in order to simplify the calculation. Then the full loss function for the landmark branch becomes:
-\begin{equation}
-  l_{LM} = M - \frac{1}{N_B} \sum_{i=1}^{N_B} \log{p_i}
-\end{equation}
+%% \begin{equation}
+%%   M = \frac{1}{\bar{N_{B_j}}} \sum_{j=1}^{N_L}  \sum_{i \in B_j} (\hat{x_{i,j}} - x_{i,j})^2 + (\hat{y_{i,j}} - y_{i,j})^2
+%% \end{equation}
+%% where $\bar{N_{B_j}}$ is the mean number of examples containing each landmark, in order to simplify the calculation. Then the full loss function for the landmark branch becomes:
+%% \begin{equation}
+%%   l_{LM} = M - \frac{1}{N_B} \sum_{i=1}^{N_B} \log{p_i}
+%% \end{equation}
 
-\paragraph{(F) Consensus Learning and Feedback}
+\paragraph{(E) Consensus Learning and Feedback}
 
@@
 
-As we have two training sets, each of which contain different groundtruth labels, we adopt an alternate training schedule to optimise our model. \emph{TODO}
+As we have two training sets, each of which contain different groundtruth labels.
 
@@
 
+\subsection{Re-ranking}
+
+\emph{TODO}
+
 \section{Experiments}
+
+We conduct a number of experiments to explore the performance of our method.
+First we exploit a number of widely available vehicle ID benchmark datasets in order to assess the benefit of each of the branches of our model independently, and altogether.
+Then we compare the performance of our model to other current work by looking at our performance in the NVIDIA AI City Challenge 2019 Task 2 (Vehicle Re-identification).
+As our method includes a branch that predicts vehicle orientation in addition to identity, our model requires data that contains the orientation labels for training.
+As a result, we include the VeRI776 dataset \cite{} in the training set for all our experiments.
+
+\subsection{Implementation Details}
+
+We employ the ResNet50 \cite{} network architecture as the base of our model.
+
+Details:
+- Learning rate of ...
+- Batch size 16?
+- Number of epochs.
+
+\subsection{Vehicle Benchmark Datasets}
+
+\begin{table}
+  \begin{tabular}{l || c | c || c | c }
+    \hline
+    \multirow{2}{*}{Method} & \multicolumn{2}{c ||}{VeRi776} & \multicolumn{2}{c}{VeRi776+VehicleID} \\
+    \cline{2-5}
+    & mAP & Rank-1 & mAP & Rank-1 \\
+    \hline
+    DPFL \cite{kanaci2018vehicle} & \\
+    \hline
+    MTML-S & \\
+    MTML-O & \\
+    MTML-G & \\
+    \hline
+    MTML-SG & \\
+    MTML-OG & \\
+    MTML-OSG & \\
+    \hline
+
+  \end{tabular}
+  \caption{}
+  \label{T:benchmark_results}
+\end{table}
+
+\subsection{NVIDIA AI City Challenge 2019}
+
+We participated in Task 2 of the NVIDIA AI City Challenge 2019.
+The aim of this task was attempt city-scale multi-camera vehicle re-identification.
+Multiple cameras were placed at multiple intersections and no camera information was provided about the images.
+
+\begin{table}
+  \begin{tabular}{l || c | c}
+
+  \end{tabular}
+  \caption{}
+  \label{T:aicity_results}
+\end{table}
+
+\subsection{Analysis}
 

### 2019-04-25 paper.tex
Start to add more to experiments section and update training algo.

@@
 \usepackage{multirow}
+
+\def\x{{\mathsf x}}
 
@@
 %%%%%%%%% TITLE
-\title{Multi-task Mutual Learning for Vehicle Re-Identification}
+\title{Multi-Task Mutual Learning for Vehicle Re-Identification}
 
@@
 Both training sets contain the associated identity class labels $\mathcal{Y}_1=\{y_i\}_{i=1}^N$ and $\mathcal{Y}_2=\{y_i\}_{i=1}^M$, where $y_i \in \left[1,...,N_{id}\right]$ for $N_{id}$ distinct vehicle idenities spanning the two training sets.
-However, in addition, $\mathcal{I}_1$ also contains orientation and landmark position labels $\mathcal{O}=\{o_i\}_{i=1}^N$ and $\mathcal{L}=\{\mathbf{l_i}\}_{i=1}^N$, where $o_i \in \left[1,...,N_O\right]$ is the orientation (for $N_O$ possible orientations), and  $\mathbf{l_i}=\{\left(x_{i,1},y_{i,1}\right),...,\left(x_{i,L},y_{i,L}\right)\}$ defines the position of $N_L$ keypoint landmarks for the vehicle within image $\mathbf{I}_i$, which we normalise according to the image size so that $x,y \in [0,1]$
+However, in addition, $\mathcal{I}_1$ also contains orientation labels, $\mathcal{O_1}=\{o_i\}_{i=1}^N$, where $o_i \in \left[1,...,N_O\right]$ is the orientation (for $N_O$ possible orientations).
+%and landmark position labels $\mathcal{L_1}=\{\mathbf{l_i}\}_{i=1}^N$ $\mathbf{l_i}=\{\left(x_{i,1},y_{i,1}\right),...,\left(x_{i,L},y_{i,L}\right)\}$ defines the position of $N_L$ keypoint landmarks for the vehicle within image $\mathbf{I}_i$, which we normalise according to the image size so that $x,y \in [0,1]$
 
@@
 
-As we have two training sets, each of which contain different groundtruth labels.
+In order to train our model, we combine both training sets, $\mathcal{I}_1$ and $\mathcal{I}_2$, and employ batches that contain both images with and without orientation labelling.
 
@@
   \begin{algorithmic}
-    \REQUIRE{Training sets $\mathcal{I}_1$ $\mathcal{I}_2$, labels $\mathcal{Y}_1$\
-      $\mathcal{O}$ $\mathcal{L}$ $\mathcal{Y}_2$, model $\mathcal{M}$}
+    \REQUIRE{Training sets $\mathcal{I}_1$ $\mathcal{I}_2$, labels $\mathcal{Y}_1$ $\mathcal{Y}_2$\
+      $\mathcal{O}_1$, model $\mathcal{M}$}
     \STATE{$\bullet$ Initialise network branches with pre-trained ImageNet weights}
@@
 
-      \FOR{each training set $\mathcal{I} \in (\mathcal{I}_1,\mathcal{I}_2)$}
         \STATE{$\bullet$ Feed-forward through model to obtain all branch identity classification \
-        predictions on images in $\mathcal{I}$}
-
-        \IF{$\mathcal{I}$ has associated $\mathcal{O}$ and $\mathcal{L}$}
-          \STATE{$\bullet$ Feed-forward to obtain orientation classification and landmark regression \
-        predictions}
-        \ENDIF
-
-        \STATE{$\bullet$ Fuse features and perform consensus identity classification predictions}
-        \STATE{$\bullet$ Calculate hard and soft losses for each branch and backpropagate to update weights}
-        \STATE{$\bullet$ Calculate hard and soft losses for the consensus branch and backpropagate}
-
-      \ENDFOR
+          predictions on images in $\mathcal{I}_1$ and $\mathcal{I}_2$}
+        \STATE{$\bullet$ Feed-forward to obtain orientation classification predictions on $\mathcal{I}_1$}
+        \STATE{$\bullet$ Fuse features and perform consensus identity classification predictions on both training sets}
+        \STATE{$\bullet$ Calculate hard and soft losses identity losses for each branch and backpropagate to update weights}
+        \STATE{$\bullet$ Calculate orientation losses using labels for $\mathcal{I}_1$ and backpropagate to update weights on the orientation branch}
+        \STATE{$\bullet$ Calculate hard and soft identity losses for the consensus branch and backpropagate}
      \ENDFOR
@@
 Details:
-- Learning rate of ...
-- Batch size 16?
+- Learning rate of 0.0001
+- Batch size 8
 - Number of epochs.
+- Adam optimiser with exponential decay rates set as follows: $\beta_1=0.9$ and $\beta_2=0.999$.
+- The two scales used: standard $224\x224$ and small (for multiscale) $160\x160$.
 
-\subsection{Vehicle Benchmark Datasets}
+We measure the performance of our vehicle re-identification methods according to the standard Cumulative Matching Characteristic (CMC) and mean Average Precision (mAP).
+The CMC is computed on each individual rank $k$ as the cumulative percentage of correct matches appearing
+at ranks $\leq k$.
+The mAP is calculated as the mean over all query images of the Average Precision, which itself is calculated as the precision cut-off at each correct recalled image position averaged over all possible correct gallery images \cite{}.
+
+\subsection{Vehicle Re-identification Datasets}
+
+\paragraph{VeRi776}
+
+\paragraph{VehicleID}
+
+\paragraph{BoxCars21k}
+
+\paragraph{CompCars}
 
 \begin{table}
-  \begin{tabular}{l || c | c || c | c }
+  \centering
+  \begin{tabular}{l || c | c | c }
     \hline
-    \multirow{2}{*}{Method} & \multicolumn{2}{c ||}{VeRi776} & \multicolumn{2}{c}{VeRi776+VehicleID} \\
-    \cline{2-5}
-    & mAP & Rank-1 & mAP & Rank-1 \\
+    Method & mAP & Rank-1 & Rank-5 \\
     \hline
@@
     \hline
+    MTML-OSG+ReRank & \\
+    \hline
+  \end{tabular}
+  \caption{Trained/tested on VeRi776 only}
+  \label{T:benchmark_results_veri}
+\end{table}
 
+\begin{table*}
+  \centering
+  \begin{tabular}{l || c | c || c | c || c | c }
+    \hline
+    \multirow{2}{*}{Method} & \multicolumn{2}{c}{Small} & \multicolumn{2}{c}{Medium} &\multicolumn{2}{c}{Large} \\
+    \cline{2-7}
+    & mAP & Rank-1 & mAP & Rank-1 & mAP & Rank-1 \\
+    \hline
+    DPFL \cite{kanaci2018vehicle} & \\
+    \hline
+    MTML-S & \\
+    MTML-O & \\
+    MTML-G & \\
+    \hline
+    MTML-SG & \\
+    MTML-OG & \\
+    MTML-OSG & \\
+    \hline
+    MTML-OSG+ReRank & \\
+    \hline
   \end{tabular}
-  \caption{}
-  \label{T:benchmark_results}
-\end{table}
+  \caption{Trained on VeRi776+VehicleID, tested on VehicleID}
+  \label{T:benchmark_results_vehicleid}
+\end{table*}
 
@@
 \begin{table}
+  \centering
   \begin{tabular}{l || c | c}

### 2019-04-25 paper.tex
Add in some other results for comparison, and update the consensus branch info. Plus add author names and other minor changes.

@@
 \usepackage{multirow}
+\usepackage{arydshln}
 
@@
 
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
+\author{Georgia Rajamanoharan\\
+Vision Semantics Ltd\\
+{\tt\small georgia@visionsemantics.com}
 % For a paper whose authors are all at the same institution,
@@
 \and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
+Aytac Kanaci \hspace{0.7cm}
+%Queen Mary University of London\\
+%{\tt\small secondauthor@i2.org}
+%\and
+Minxian Li  \hspace{0.7cm}
+%Queen Mary University of London\\
+%{\tt\small secondauthor@i2.org}
+%\and
+Shaogang Gong\\
+Queen Mary University of London\\
+{\tt\small \{a.kanaci,m.li,s.gong\}@qmul.ac.uk }
 }
@@
 
-In this paper we propose a new mutual learning based network architecture, that aims to simulataneously learn a number of tasks and then use consensus learning to build an improved representation for the purpose of vehicle re-identification.
+In this paper we propose a new mutual learning based network architecture, that aims to simulataneously learn a number of tasks, plus a consensus, to build an improved representation for the purpose of vehicle re-identification.
 
@@
 This is done via feature fusion of the final convolutional feature maps from all branches for consensus learning.
-As our branches are based on the MobileNet architecture, these feature maps are formed via an average pooling operation which result in feature vectors of length $1280$.
-Hence our fused features are of length $6400$.
-This is then passed to one additional identity softmax classification layer, again employed with cross entropy loss.
+As our branches are based on the ResNet50 architecture, these feature maps are formed via an average pooling operation which result in feature vectors of length $2048$.
+Hence our fused features are of length $8192$.
+We then add one additional fully connected layer, of size $1024$, and the output of this passed to a final identity softmax classification layer, again employed with cross entropy loss.
 Hence:
@@
 As our method includes a branch that predicts vehicle orientation in addition to identity, our model requires data that contains the orientation labels for training.
-As a result, we include the VeRI776 dataset \cite{} in the training set for all our experiments.
+As a result, we include the VeRI776 dataset \cite{liu2016veri} in the training set for all our experiments.
 
@@
     \hline
-    DPFL \cite{kanaci2018vehicle} & \\
+    MSVF \cite{kanaci2018vehicle} & 49.3 & 88.6 & - \\
+    OIFE \cite{wang2017orientation} & 51.4 & 68.3 & 89.7 \\
+    S-CNN+P-LSTM \cite{Shen_2017_ICCV} & 58.3 & 83.5 & 90.0 \\
+    MTCRO (no ReRank) \cite{xu2018framework} & 61.6 & 87.2 & 94.2 \\
+    MTCRO (ReRank) \cite{xu2018framework} & 62.6 & 88.0 & 94.6 \\
     \hline
@@
     MTML-G & \\
-    \hline
+    \hdashline
     MTML-SG & \\
@@
     MTML-OSG & \\
-    \hline
-    MTML-OSG+ReRank & \\
+    \hdashline
+    MTML-OSG (ReRank) & \\
     \hline
@@
     \hline
-    DPFL \cite{kanaci2018vehicle} & \\
-    \hline
     MTML-S & \\
@@
     MTML-OSG & \\
-    \hline
+    \hdashline
     MTML-OSG+ReRank & \\

### 2019-04-25 paper.tex
Add some of our results and minor changes.

@@
 In order to train our model, we combine both training sets, $\mathcal{I}_1$ and $\mathcal{I}_2$, and employ batches that contain both images with and without orientation labelling.
+The full training algorithm can be seen in Algorithm \ref{A:model_training}.
 
 \begin{algorithm}[t]
-  \caption{The model training algorithm}
-  \label{A:model_training}
   \begin{algorithmic}
@@
   \end{algorithmic}
+  \caption{The MTML training algorithm.}
+  \label{A:model_training}
 \end{algorithm}
@@
     S-CNN+P-LSTM \cite{Shen_2017_ICCV} & 58.3 & 83.5 & 90.0 \\
-    MTCRO (no ReRank) \cite{xu2018framework} & 61.6 & 87.2 & 94.2 \\
-    MTCRO (ReRank) \cite{xu2018framework} & 62.6 & 88.0 & 94.6 \\
+    MTCRO \cite{xu2018framework} & 61.6 & 87.2 & 94.2 \\
     \hline
@@
     MTML-OG & \\
-    MTML-OSG & \\
-    \hdashline
-    MTML-OSG (ReRank) & \\
+    MTML-OSG & \bf{61.8} & \bf{90.3} & \bf{95.4} \\
+    \hline
+    MTCRO (ReRank) \cite{xu2018framework} & 62.6 & 88.0 & \bf{94.6} \\
+    MTML-OSG (ReRank) & \bf{65.8} & \bf{91.9} & 94.0 \\
     \hline

### 2019-04-30 paper.tex
More changes including more results.

@@
 \usepackage{arydshln}
+\usepackage{subcaption}
 
@@
 
+\begin{figure*}
+  \begin{subfigure}{.6\textwidth}
+    \includegraphics[width=\linewidth,trim=5cm 11cm 5cm 11cm,clip=true]{images/veri_orients.pdf}
+  \end{subfigure}
+  \begin{subfigure}{.4\textwidth}
+    \centering
+    \begin{tabular}{c | c | c}
+      \hline
+      Index & Orientation & Colour \\
+      \hline
+      0 & front & \textcolor{red}{red} \\
+      1 & rear & \textcolor{blue}{blue}  \\
+      2 & left  & - \\
+      3 & left front & \textcolor{cyan}{cyan}  \\
+      4 & left rear & \textcolor{yellow}{yellow}  \\
+      5 & right  & - \\
+      6 & right front & \textcolor{green}{green} \\
+      7 & right rear & \textcolor{black}{black} \\
+      \hline
+    \end{tabular}
+  \end{subfigure}
+  \caption{Examples from the VeRi776 dataset with the orientation labels provided in \cite{wang2017orientation} (best viewed in colour).}
+  \label{T:veri_veh_orientations}
+\end{figure*}
+
 \section{Multi-modal Vehicle Re-identification}
 
-In order to perform Re-ID of previously unseen query vehicles, the aim of our model is to learn an feature embedding that allows for accurate retrivals based on distance (\eg L1) from the query image representation.
-In order to perform this task, we utilise training data containing a number of different labels: identity class labels, vehicle orientation class labels, and landmark position labels for a number of specific keypoints.
+In order to perform Re-ID of previously unseen query vehicles, the aim of our model is to learn a feature embedding that allows for accurate retrivals based on distance (\eg L1) from the query image representation.
+In order to perform this task, we utilise training data containing a number of different labels: identity class labels as well as vehicle orientation class labels.
+%and landmark position labels for a number of specific keypoints
 We assume two sets of training examples $\mathcal{I}_1 = \{\mathbf{I_i}\}_{i=1}^N$ and $\mathcal{I}_2 = \{\mathbf{I_i}\}_{i=1}^M$, containing $N$ and $M$ training images respectively.
@@
 
-In order to perform accurate re-ID, we use this data to build a model constructed from a number of branches, each of which is tasked with learning a specific aspect of the data. \emph{TODO expand}
+In order to perform accurate re-ID, we use this data to build a model constructed from a number of branches, each of which is tasked with learning a specific aspect of the data concurrently.
+The branches of the model are as follows: A) Identity classification B) Identity classification from a scaled image C) Identity from grayscale image D) Identity plus the vehicles' orienations.
+The individual branches then form a consensus prediction on the identity of the training examples, and this consensus is then employed for regulation of the individual branches.
 
@@
   \includegraphics[width=\linewidth,trim=0cm 8cm 0cm 0cm,clip=true]{images/system_overview_orient_only.pdf}
-  \label{F:overview}
   \caption{An overview of our proposed model (best viewed in colour). (A) Vehicle identity branch (B) Multi-scale analysis branch (C) Grayscale analysis branch (D) Vehicle orientation branch
@@
 Soft target consensus feedback loss propagation shown in \textcolor{green}{green}.}
+  \label{F:overview}
 \end{figure*}
@@
 
+We employ a number of previously released Vehicle Re-ID datasets in our experiments, in order to train and test our method extensively.
+Firstly we conduct experiments on two benchmark datasets: VeRi776 and VehicleID.
+Firstly we train and test only the VeRi776 dataset, for comparison with previous state-of-the-art methods.
+And secondly we train on both the VeRi776 and VehicleID datasets, and then test on the VehicleID, for all three testsets: small, medium and large.
+We conduct the latter experiment in this was due to the fact that our method requires some training data with orientation labels.
+As VeRi776 is the only dataset with labels of this kind, we must therefore include it in the training.
+
+\begin{table}
+  \begin{tabular}{c | c | c | c}
+    TODO
+  \end{tabular}
+  \caption{Details of the datasets employed for train and test.}
+  \label{T:dataset_details}
+\end{table}
+
 \paragraph{VeRi776}
@@
 \paragraph{CompCars}
+
+Table \ref{T:benchmark_results_veri} shows the results of the first experiment, where we train and test only on the VeRi776 dataset.
+As can be seen, our model achieves state-of-the-art mAP and Rank-1 scores on this dataset, of ...
+and ...
+respectively.
+
+After 100 epochs
 
@@
     \hline
-    MTML-S & \\
+    MTML-S & 59.4 & 89.7 & 95.1 \\
     MTML-O & \\
@@
     \hdashline
-    MTML-SG & \\
+    MTML-SG & 63.4 & 91.1 & 95.4 \\
     MTML-OG & \\

### 2019-05-02 paper.tex
Add details about the different datasets.
Add introduction

--- 2019-04-25 paper.tex
@@
 \usepackage{multirow}
-\usepackage{arydshln}
+% \usepackage{arydshln}
+% \usepackage{todonotes}
 
@@
 \setcounter{page}{4321}
+
+%% helper definitions
+\def\eg{\emph{e.g.\hspace{0.3em}}}
+\def\Eg{\emph{E.g.\hspace{0.3em}}}
+\def\ie{\emph{i.e.\hspace{0.3em}}}
+\def\etal{\emph{et al.\hspace{0.3em}}}
+
+% TODO
+\newcommand{\todo}[1]{}
+\renewcommand{\todo}[1]{{\color{red} TODO: {#1}}}
+
 \begin{document}
@@
 
-Vehicle re-identification (re-id) aims at searching vehicle instances across nonoverlapping camera views by image matching.
-Influenced by the recent extensive studies on person re-id \cite{gong2014re}, vehicle re-id has started to gain increasing attention in the past two years, and a number of vehicle databases and additional labelling are now available to facilitate this research \cite{liu2016vehicleid,liu2016veri,yang2015large,kanaci2018vehicle,wang2017orientation}.
-This area promises the potential for more flexible means for vehicle recognition and search than Automatic Number Plate Recognition (ANPR).
-However, vehicle re-id by visual appearance is a
+%%% Background and motivation
+As the ubiquitousness of surveillance cameras capturing vehicle in transport in
+cities and highways increase, the need for analyzing this visual data has
+become an interest in computer vision. With the advent of autonomous driving
+and smart city applications the need for accurately analyzing vehicles in these
+scenarios with related computer vision tasks \ie detection, classification and
+pose estimation as well as re-identification is ever-increasing.
+
+Vehicle re-identification (re-ID) aims at searching a target vehicle
+(identity) across non-overlapping camera views by image matching.  
+Vehicle re-identification received less attention than person re-identification
+which is been studied extensively \cite{gong2014re, Li2018Harmonious,
+chen2017person}.\todo{add more citation}
+
+As a unique ID of a vehicle, license plate has been widely used for vehicle
+re-ID. However, license plate recognition is quite sensitive to image quality,
+camera view and occlusion. Furthermore, license plate may be removed,
+altered even faked in some cases, making it unreliable to identify a vehicle
+simply by its license plate. Therefore, vehicle re-ID by visual appearance is
+of great practical value in real-world applications such as smart cities.
+
+A related problem to vehicle re-identification is fine-grained vehicle model 
+classification such as ``Audi A4 2014''\cite{yang2015compcars}.  
+However, the granularity of vehicle re-identification task is much finer
+since the ideal target is to search a specific vehicle rather than a model, in
+which the image instances of the same vehicle (identity) forms a separate
+class.
+%%% Vehicle re-id challenges 
+However,
+vehicle re-id by visual appearance is a
 challenging task due to the very similar appearance of different vehicle instances
-of the same model type and colour, and a significant visual appearance variation
-of the same vehicle instance in different camera views \cite{}.
+of the same model type and color, and a significant visual appearance variation
+of the same vehicle instance in different camera views. In other words
+large intra-instance differences of the same vehicle in different cameras,
+and subtle inter-instance differences between different vehicles in the same
+view, considering thousands of vehicles in a large scale smart city setting is
+the main challenge of vehicle re-ID. Moreover, unlike person re-id 
+orientation of vehicles results in self occlusion and drastic visual geometry
+changes where in person re-id visual geometry or texture of the person's
+appearance (wear) will not change.
+% re-ID problem. A human body is usually upright, thus the texture or color of
+% his/her wear will not change severely in different views. Deploying the
+% person re-ID methods for vehicles directly cannot obtain satisfactory
+% performance.
+% Due to the fact that vehicles are rigid objects, unlike people, the orientation
+% of the vehicle can alter very predictably the appearance of in a particular
+% viewpoint.
 
-Due to the fact that vehicles are rigid objects, unlike people, the orientation of the vehicle can alter very predictably the appearance of in a particular viewpoint.
-\emph{TODO motivation and related work}
+% This area promises the potential for more flexible means for vehicle
+% recognition and search than Automatic Number Plate Recognition (ANPR).
 
-In this paper we propose a new mutual learning based network architecture, that aims to simulataneously learn a number of tasks, plus a consensus, to build an improved representation for the purpose of vehicle re-identification.
+% be found as an instance-level object search problem.
+
+%%% matching probe gallery
+Formally re-ID  aims to find
+target images of the same identity in a large gallery set given a probe image. 
+In order to match appearances of objects, firstly we need to obtain an
+embedding for the objects. A
+match is then performed by using a suitable distance metric expressing the
+closeness of two objects in an embedding space. A good embedding should be
+invariant to illumination, scale and viewpoint changes.
+
+%%% we use CNNs
+Recently, Convolutional Neural Network (CNN) has achieved state-of-the-art
+performance in various computer vision 
+recognition tasks, such as large-scale image classification 
+face recognition  and person re-ID.
+With the supervision of a carefully designed objective loss, typically
+cross-entropy and/or triplet loss
+% contrastive loss or triplet loss
+CNN can learn efficient feature embedding
+
+%%% Datasets and SOTA
+Influenced by the recent advancements on person re-id vehicle re-id has started
+to gain increasing attention, 
+and a number of vehicle databases and additional labeling are now available to
+facilitate this research
+ including 
+ VeRi-776\cite{Liu2016icme-veri, Liu2016eccv_veri}  ,
+ VehicleID\cite{liu2016vehicleid} and VRIC\cite{kanaci2018vehicle} and methods
+ specific to vehicle re-ID becoming more frequent in various venues
+ \cite{wang2017orientation, Shen_2017_ICCV, Zhou2018VAMI}.
+
+%%% Our method:
+In this paper we propose a new mutual learning based network architecture, that
+aims to simultaneously learn a number of tasks, plus a consensus, to build an
+improved representation for the purpose of vehicle re-identification.
+% Second, we propose to leverage multi-task learning to gen- erate discriminative
+% feature representation by the joint op- timization of group sensitive triplet
+% loss and softmax loss, which can be well applied to accomplish large scale
+% vehicle re-identification towards real applications.
+
+\section{Related Work}
 
@@
 
-In order to perform Re-ID of previously unseen query vehicles, the aim of our model is to learn an feature embedding that allows for accurate retrivals based on distance (\eg L1) from the query image representation.
-In order to perform this task, we utilise training data containing a number of different labels: identity class labels, vehicle orientation class labels, and landmark position labels for a number of specific keypoints.
-We assume two sets of training examples $\mathcal{I}_1 = \{\mathbf{I_i}\}_{i=1}^N$ and $\mathcal{I}_2 = \{\mathbf{I_i}\}_{i=1}^M$, containing $N$ and $M$ training images respectively.
-Both training sets contain the associated identity class labels $\mathcal{Y}_1=\{y_i\}_{i=1}^N$ and $\mathcal{Y}_2=\{y_i\}_{i=1}^M$, where $y_i \in \left[1,...,N_{id}\right]$ for $N_{id}$ distinct vehicle idenities spanning the two training sets.
-However, in addition, $\mathcal{I}_1$ also contains orientation labels, $\mathcal{O_1}=\{o_i\}_{i=1}^N$, where $o_i \in \left[1,...,N_O\right]$ is the orientation (for $N_O$ possible orientations).
+In order to perform Re-ID of previously unseen query vehicles, the aim of our
+model is to learn an feature embedding that allows for accurate retrivals based
+on distance (\eg L1) from the query image representation. In order to perform
+this task, we utilise training data containing a number of different labels:
+identity class labels, vehicle orientation class labels, and landmark position
+labels for a number of specific keypoints. We assume two sets of training
+examples 
+$\mathcal{I}_1 = \{\mathbf{I_i}\}_{i=1}^N$ 
+and 
+$\mathcal{I}_2 = \{\mathbf{I_i}\}_{i=1}^M$, 
+containing $N$ and $M$ training images respectively. Both training sets contain the associated identity class labels 
+$\mathcal{Y}_1=\{y_i\}_{i=1}^N$ and $\mathcal{Y}_2=\{y_i\}_{i=1}^M$, 
+where $y_i \in \left[1,...,N_{id}\right]}$ for $N_{id}$ 
+distinct vehicle idenities spanning the two training sets. However, in
+addition, $\mathcal{I}_1$ also contains orientation labels,
+$\mathcal{O_1}=\{o_i\}_{i=1}^N$, where $o_i \in \left[1,...,N_O\right]$ 
+is the orientation (for $N_O$ possible orientations).
+
 %and landmark position labels $\mathcal{L_1}=\{\mathbf{l_i}\}_{i=1}^N$ $\mathbf{l_i}=\{\left(x_{i,1},y_{i,1}\right),...,\left(x_{i,L},y_{i,L}\right)\}$ defines the position of $N_L$ keypoint landmarks for the vehicle within image $\mathbf{I}_i$, which we normalise according to the image size so that $x,y \in [0,1]$
 
-In order to perform accurate re-ID, we use this data to build a model constructed from a number of branches, each of which is tasked with learning a specific aspect of the data. \emph{TODO expand}
+In order to perform accurate re-ID, we use this data to build a model
+constructed from a number of branches, each of which is tasked with learning a
+specific aspect of the data. \emph{TODO expand}
 
@@
     MTML-G & \\
-    \hdashline
+    % \hdashline
     MTML-SG & \\
@@
     MTML-OSG & \\
-    \hdashline
+    % \hdashline
     MTML-OSG+ReRank & \\

### 2019-05-02 paper.tex

@@
 % \usepackage{arydshln}
-% \usepackage{todonotes}
+\usepackage{subcaption}
 
@@
  including 
- VeRi-776\cite{Liu2016icme-veri, Liu2016eccv_veri}  ,
+ VeRi-776\cite{Liu2016icme-veri, Liu2016eccv_veri},
  VehicleID\cite{liu2016vehicleid} and VRIC\cite{kanaci2018vehicle} and methods
@@
 %%% Our method:
+\todo{Expand near submission}
 In this paper we propose a new mutual learning based network architecture, that
@@
 
+\begin{figure*}
+  \begin{subfigure}{.6\textwidth}
+    \includegraphics[width=\linewidth,trim=5cm 11cm 5cm 11cm,clip=true]{images/veri_orients.pdf}
+  \end{subfigure}
+  \begin{subfigure}{.4\textwidth}
+    \centering
+    \begin{tabular}{c | c | c}
+      \hline
+      Index & Orientation & Colour \\
+      \hline
+      0 & front & \textcolor{red}{red} \\
+      1 & rear & \textcolor{blue}{blue}  \\
+      2 & left  & - \\
+      3 & left front & \textcolor{cyan}{cyan}  \\
+      4 & left rear & \textcolor{yellow}{yellow}  \\
+      5 & right  & - \\
+      6 & right front & \textcolor{green}{green} \\
+      7 & right rear & \textcolor{black}{black} \\
+      \hline
+    \end{tabular}
+  \end{subfigure}
+  \caption{Examples from the VeRi776 dataset with the orientation labels provided in \cite{wang2017orientation} (best viewed in colour).}
+  \label{T:veri_veh_orientations}
+\end{figure*}
+
 \section{Multi-modal Vehicle Re-identification}
 
-In order to perform Re-ID of previously unseen query vehicles, the aim of our
-model is to learn an feature embedding that allows for accurate retrivals based
-on distance (\eg L1) from the query image representation. In order to perform
-this task, we utilise training data containing a number of different labels:
-identity class labels, vehicle orientation class labels, and landmark position
-labels for a number of specific keypoints. We assume two sets of training
-examples 
-$\mathcal{I}_1 = \{\mathbf{I_i}\}_{i=1}^N$ 
-and 
-$\mathcal{I}_2 = \{\mathbf{I_i}\}_{i=1}^M$, 
-containing $N$ and $M$ training images respectively. Both training sets contain the associated identity class labels 
-$\mathcal{Y}_1=\{y_i\}_{i=1}^N$ and $\mathcal{Y}_2=\{y_i\}_{i=1}^M$, 
-where $y_i \in \left[1,...,N_{id}\right]}$ for $N_{id}$ 
-distinct vehicle idenities spanning the two training sets. However, in
-addition, $\mathcal{I}_1$ also contains orientation labels,
-$\mathcal{O_1}=\{o_i\}_{i=1}^N$, where $o_i \in \left[1,...,N_O\right]$ 
-is the orientation (for $N_O$ possible orientations).
-
+In order to perform Re-ID of previously unseen query vehicles, the aim of our model is to learn a feature embedding that allows for accurate retrivals based on distance (\eg L1) from the query image representation.
+In order to perform this task, we utilise training data containing a number of different labels: identity class labels as well as vehicle orientation class labels.
+%and landmark position labels for a number of specific keypoints
+We assume two sets of training examples $\mathcal{I}_1 = \{\mathbf{I_i}\}_{i=1}^N$ and $\mathcal{I}_2 = \{\mathbf{I_i}\}_{i=1}^M$, containing $N$ and $M$ training images respectively.
+Both training sets contain the associated identity class labels $\mathcal{Y}_1=\{y_i\}_{i=1}^N$ and $\mathcal{Y}_2=\{y_i\}_{i=1}^M$, where $y_i \in \left[1,...,N_{id}\right]$ for $N_{id}$ distinct vehicle idenities spanning the two training sets.
+However, in addition, $\mathcal{I}_1$ also contains orientation labels, $\mathcal{O_1}=\{o_i\}_{i=1}^N$, where $o_i \in \left[1,...,N_O\right]$ is the orientation (for $N_O$ possible orientations).
 %and landmark position labels $\mathcal{L_1}=\{\mathbf{l_i}\}_{i=1}^N$ $\mathbf{l_i}=\{\left(x_{i,1},y_{i,1}\right),...,\left(x_{i,L},y_{i,L}\right)\}$ defines the position of $N_L$ keypoint landmarks for the vehicle within image $\mathbf{I}_i$, which we normalise according to the image size so that $x,y \in [0,1]$
 
-In order to perform accurate re-ID, we use this data to build a model
-constructed from a number of branches, each of which is tasked with learning a
-specific aspect of the data. \emph{TODO expand}
+In order to perform accurate re-ID, we use this data to build a model constructed from a number of branches, each of which is tasked with learning a specific aspect of the data concurrently.
+The branches of the model are as follows: A) Identity classification B) Identity classification from a scaled image C) Identity from grayscale image D) Identity plus the vehicles' orienations.
+The individual branches then form a consensus prediction on the identity of the training examples, and this consensus is then employed for regulation of the individual branches.
+>>>>>>> e5e018ecb6db264c0f87b6bfce9aaf7c51b0ff67
 
@@
 
-\paragraph{VeRi776}
+We employ a number of previously released Vehicle Re-ID datasets in our experiments, in order to train and test our method extensively.
+Firstly we conduct experiments on two benchmark datasets: VeRi776 and VehicleID.
+Firstly we train and test only the VeRi776 dataset, for comparison with previous state-of-the-art methods.
+And secondly we train on both the VeRi776 and VehicleID datasets, and then test on the VehicleID, for all three testsets: small, medium and large.
+We conduct the latter experiment in this was due to the fact that our method requires some training data with orientation labels.
+As VeRi776 is the only dataset with labels of this kind, we must therefore include it in the training.
 
-\paragraph{VehicleID}
+\begin{table*}
+  \centering
+  \begin{tabular}{c || c | c | c || c | c || c | c}
+    \hline
+    \multirow{2}{*}{Dataset} & \multicolumn{3}{c||}{Training} & \multicolumn{2}{c||}{Probe} & \multicolumn{2}{c}{Gallery} \\
+    \cline{2-7}
+    & \#IDs& \#Imgs & \#Orients & \#IDs & \#Imgs & \#IDs & \#Imgs \\
+    \hline
+    VeRi-776 \cite{} & 576 & 30188 & 8 & 200 & 1678 & 200 & 11579 \\
+    VehicleID \cite{} & 13164 & 100182 & - & 2400 & 17638 & 2400 & 2400 \\
+    BoxCars \cite{} & 21250 & 63750 & -  & - & - & - & - \\
+    CompCars \cite{} & 1118 & 31148 & - & - & - & - & - \\
+    AICity2019 \cite{} & \\
+    \hline
+  \end{tabular}
+  \caption{Details of the datasets employed for train and test.}
+  \label{T:dataset_details}
+\end{table*}
 
-\paragraph{BoxCars21k}
+Table \ref{T:benchmark_results_veri} shows the results of the first experiment, where we train and test only on the VeRi776 dataset.
+As can be seen, our model achieves state-of-the-art mAP and Rank-1 scores on this dataset, of ...
+and ...
+respectively.
 
-\paragraph{CompCars}
+After 100 epochs
 
@@
     % \hdashline
-    MTML-SG & \\
+    MTML-SG & 63.4 & 91.1 & 95.4 \\
     MTML-OG & \\

### 2019-05-02 paper.tex

@@
 
+\noindent {\bf Vehicle Model Classification }
+One closely related problem to re-identification is vehicle model
+classification
+\cite{liao2015exploiting,gu2013car,lin2014jointly,yang2015compcars,sochor2016boxcars,hu2017deep}.
+But, the two problems are usually studied independently.
+For example, Yang et al. \cite{yang2015compcars} propose a part attributes driven 
+vehicle model recognition. 
+They also contribute a large comprehensive car dataset named ``CompCars''
+with model class labels but without vehicle identity labels. 
+More recently, Hu et al. \cite{hu2017deep} formulate a deep CNN framework capable of 
+selecting spatial salient vehicle parts in order to learn more
+discriminative model representations without explicit parts annotations, with
+
+\noindent {\bf Vehicle Re-Identification. }
+Whist vehicle re-id is less studied than person re-id
+\cite{gong2014person,li2014deepreid,ahmed2015improved,xiao2016learning,li2017person,sun2017svdnet,li2018harmonious,zhong2017camera},
+there are a handful of existing methods.
+%Notably, Feris \etal \cite{feris2012large} proposed an attribute-based re-id method. 
+%The vehicles are firstly classified by different attributes like car model types and colours. The re-id matching is then conducted in the attribute space.
+%%
+%Dominik \etal \cite{zapletal2016vehicle}
+%used 3D bounding boxes for rectifying car images and then concatenate colour histogram features of vehicle image pairs. 
+%A binary linear SVM model is then trained to verify whether a pair of images have the same identity.
+%%
+%Both methods rely heavily on weak hand-crafted visual features in a
+%complex multi-step based approach, suffering from weak discriminative model generalisation.
+
+Recently, deep learning techniques have been exploited to vehicle re-id.  Liu
+\etal \cite{Liu2016eccv_veri} explored a deep neural network to estimate the
+visual similarities between vehicle images.
+%Vehicle appearances, spatio-temporal information and license plates are
+%independently and incrementally used to improve the similarity function for
+%vehicle matching.  they use a deep neural network to estimate the visual
+%similarities between vehicle images for enjoying the strong representation
+%learning capacity.
+%
+Liu \etal \cite{Liu2016cvpr_drdl} also designed a Coupled Clusters Loss (CCL)
+to boost a multi-branch CNN model for vehicle re-id. 
+%
+All these methods utilize the global appearance features of vehicle images and
+ignore local discriminative regions.
+%
+To explore local information and motivated by the idea of landmark alignment
+\cite{zhang2014facial} in both face recognition \cite{taigman2014deepface} and
+human body pose estimation \cite{newell2016stacked}, Wang \etal
+\cite{Wang_2017_ICCV} considered 20 vehicle keypoints for learning and aligning
+local regions of a vehicle for re-id.  Clearly, this approach comes with extra
+cost of exhaustively labeling these keypoints in a large number of vehicle
+images, and the implicit assumption of having sufficient image
+resolution/details for computing these keypoints.
+%
+
+Additionally, 
+space-time contextual knowledge has also been exploited for vehicle re-id
+subject to structured scenes \cite{Liu2016eccv_veri,Shen_2017_ICCV}.
+Liu \etal \cite{Liu2016eccv_veri} proposed
+a spatio-temporal affinity approach for quantifying every pair of images.
+%This method is inclined to image pairs that are close to each other 
+%in both spatial and temporal domains therefore only a simplified solution.
+%
+Shen \etal \cite{Shen_2017_ICCV} further 
+incorporated spatio-temporal path information of vehicles.
+Whilst this method improves the re-id performance on the VeRi-776 dataset,
+it may not generalize to complex scene structures when the number of 
+visual spatio-temporal path proposals is very large with only weak contextual 
+knowledge available to facilitate model decision.
+
+\section{Multi-modal Vehicle Re-identification}
 \begin{figure*}
@@
 
-\section{Multi-modal Vehicle Re-identification}
-
 In order to perform Re-ID of previously unseen query vehicles, the aim of our model is to learn a feature embedding that allows for accurate retrivals based on distance (\eg L1) from the query image representation.
@@
 The individual branches then form a consensus prediction on the identity of the training examples, and this consensus is then employed for regulation of the individual branches.
->>>>>>> e5e018ecb6db264c0f87b6bfce9aaf7c51b0ff67
 

### 2019-05-02 paper.tex
Fix some merge issues and add more results. Plus some tidy ups.

@@
 \usepackage{multirow}
-% \usepackage{arydshln}
+\usepackage{arydshln}
 \usepackage{subcaption}
@@
 Whist vehicle re-id is less studied than person re-id
-\cite{gong2014person,li2014deepreid,ahmed2015improved,xiao2016learning,li2017person,sun2017svdnet,li2018harmonious,zhong2017camera},
+\cite{gong2014person,li2014deepreid,ahmed2015improved,xiao2016learning,li2017person,sun2017svdnet,Li2018Harmonious,zhong2017camera},
 there are a handful of existing methods.
@@
       0 & front & \textcolor{red}{red} \\
-      1 & rear & \textcolor{blue}{blue}  \\
+      1 & rear & -  \\
       2 & left  & - \\
@@
 
-\begin{figure*}
-  \includegraphics[width=\linewidth,trim=0cm 8cm 0cm 0cm,clip=true]{images/system_overview_orient_only.pdf}
-  \caption{An overview of our proposed model (best viewed in colour). (A) Vehicle identity branch (B) Multi-scale analysis branch (C) Grayscale analysis branch (D) Vehicle orientation branch
-    %(E) Vehicle landmark localisation branch.
-(E) Consensus learning through feature fusion.
-Feedforward signals shown in black.
-Hard target (groundtruth) loss propagation shown in \textcolor{red}{red}.
-Soft target consensus feedback loss propagation shown in \textcolor{green}{green}.}
-  \label{F:overview}
-\end{figure*}
-
 An overview of our proposed model can be seen in Figure \ref{F:overview}.
@@
 
-\paragraph{(B) Multi-scale Analysis}
+\begin{figure*}
+  \includegraphics[width=\linewidth,trim=0cm 8cm 0cm 0cm,clip=true]{images/system_overview_orient_only.pdf}
+  \caption{An overview of our proposed model (best viewed in colour). (A) Vehicle identity branch (B) Multi-scale analysis branch (C) Grayscale analysis branch (D) Vehicle orientation branch
+    %(E) Vehicle landmark localisation branch.
+(E) Consensus learning through feature fusion.
+Feedforward signals shown in black.
+Hard target (groundtruth) loss propagation shown in \textcolor{red}{red}.
+Soft target consensus feedback loss propagation shown in \textcolor{green}{green}.}
+  \label{F:overview}
+\end{figure*}
+
+\paragraph{(B) Identity from Scaled Image}
 
@@
 \]
+
 %% \paragraph{(E) Vehicle Landmark Localisation}
@@
 We employ the ResNet50 \cite{} network architecture as the base of our model.
-
-Details:
-- Learning rate of 0.0001
-- Batch size 8
-- Number of epochs.
-- Adam optimiser with exponential decay rates set as follows: $\beta_1=0.9$ and $\beta_2=0.999$.
-- The two scales used: standard $224\x224$ and small (for multiscale) $160\x160$.
+We train the model with minibatches of size 8, using the Adam optimisation technique with a learning rate of 0.0001, exponential decay rates set as follows: $\beta_1=0.9$ and $\beta_2=0.999$.
+The two image sizes used were standard $224\x224$ and small (for the scaled branch) $160\x160$.
 
@@
 Table \ref{T:benchmark_results_veri} shows the results of the first experiment, where we train and test only on the VeRi776 dataset.
-As can be seen, our model achieves state-of-the-art mAP and Rank-1 scores on this dataset, of ...
-and ...
-respectively.
+All experiments we continued for 150 epochs of training.
+As can be seen, even before re-ranking, our full model achieves state-of-the-art mAP and Rank-1 scores on this dataset, of 64.6 and 92.3 respectively.
+And after re-ranking the mAP score is increased to an impressive 68.3.
 
-After 100 epochs
+\emph{TODO more detailed discussion of results}
 
@@
     MTCRO \cite{xu2018framework} & 61.6 & 87.2 & 94.2 \\
+    MTCRO (ReRank) \cite{xu2018framework} & 62.6 & 88.0 & \bf{94.6} \\
     \hline
-    MTML-S & 59.4 & 89.7 & 95.1 \\
-    MTML-O & \\
-    MTML-G & \\
-    % \hdashline
-    MTML-SG & 63.4 & 91.1 & 95.4 \\
-    MTML-OG & \\
-    MTML-OSG & \bf{61.8} & \bf{90.3} & \bf{95.4} \\
-    \hline
-    MTCRO (ReRank) \cite{xu2018framework} & 62.6 & 88.0 & \bf{94.6} \\
-    MTML-OSG (ReRank) & \bf{65.8} & \bf{91.9} & 94.0 \\
+    MTML-S & 59.4 & 89.5 & 94.9 \\
+    MTML-O & 60.8 & 90.2 & 95.4 \\
+    MTML-G \emph{TODO} & 62.8 & 90.9 & 96.2 \\
+    \hdashline
+    MTML-SG & 63.7 & 90.6 & 95.8 \\
+    MTML-OG & 63.5 & 92.0 & \bf{96.4}\\
+    MTML-OSG & \bf{64.6} & \bf{92.3} & 95.7 \\
+    \hdashline
+    MTML-OSG (ReRank) & \bf{\emph{68.3}} & 92.0 & 94.2 \\
     \hline

### 2019-05-03 paper.tex
Update final VeRi result.
Add Jimmy's changes.

@@
 %\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{4321}
+\setcounter{page}{1}
 
@@
 %%% Background and motivation
-As the ubiquitousness of surveillance cameras capturing vehicle in transport in
-cities and highways increase, the need for analyzing this visual data has
-become an interest in computer vision. With the advent of autonomous driving
+%As the ubiquitousness of surveillance cameras capturing vehicle in transport in
+%cities and highways increase, the need for analyzing this visual data has
+%become an interest in computer vision.
+
+%% Background of vehicle re-ID
+With the development of autonomous driving
 and smart city applications the need for accurately analyzing vehicles in these
@@
 pose estimation as well as re-identification is ever-increasing.
+%
+Specially, vehicle re-identification (re-ID) attracted increasing attentions in community
+\cite{liu2016vehicleid,Liu2016cvpr_drdl,liu2016veri,Liu2016eccv_veri,
+wang2017orientation,Wang_2017_ICCV,Zhou2018VAMI},
+since it can play an important role in
+intelligent transportation system and social safety.
 
-Vehicle re-identification (re-ID) aims at searching a target vehicle
-(identity) across non-overlapping camera views by image matching.
-Vehicle re-identification received less attention than person re-identification
-which is been studied extensively \cite{gong2014re, Li2018Harmonious,
-chen2017person}.\todo{add more citation}
+%% What's vehicle re-ID?
+Vehicle re-identification task aims at searching a specific vehicle
+instance across non-overlapping camera views.
+%
+Due to the unavailability of license plate under some circumstances,
+vehicle re-ID by visual appearance is of great practical value in real-world applications such as smart cities.
+%
+This task is similar with a more popular task: person re-identification
+\cite{gong2014re,chen2017person,Li2018Harmonious,xiao2016learning,
+li2017person,wei2018person,song2018mask,chang2018multi,
+shen2018deep,zhang2017deep,shen2018person,suh2018part},
+but with more challenges:
+%% Vehicle re-ID challenges
+(1) Unlike person re-id, pose/orientation of vehicles results in self occlusion and drastic visual geometry changes, since vehicle is a kind of rigid body.
+% The same vehicle under different viewpoints are visually more diverse than person,
+This means that the same identity must be inferred with any pose/orientation of the vehicle is given.
+(2) Even the same orientation, the different identity vehicles may look very similar
+due to the similar even same vehicle model. This requires the vehicle re-id model
+to have a more powerful fine-grained recognition ability.
 
-As a unique ID of a vehicle, license plate has been widely used for vehicle
-re-ID. However, license plate recognition is quite sensitive to image quality,
-camera view and occlusion. Furthermore, license plate may be removed,
-altered even faked in some cases, making it unreliable to identify a vehicle
-simply by its license plate. Therefore, vehicle re-ID by visual appearance is
-of great practical value in real-world applications such as smart cities.
+% Existing work's problem
 
-A related problem to vehicle re-identification is fine-grained vehicle model
-classification such as ``Audi A4 2014''\cite{yang2015compcars}.
-However, the granularity of vehicle re-identification task is much finer
-since the ideal target is to search a specific vehicle rather than a model, in
-which the image instances of the same vehicle (identity) forms a separate
-class.
-%%% Vehicle re-id challenges
-However,
-vehicle re-id by visual appearance is a
-challenging task due to the very similar appearance of different vehicle instances
-of the same model type and color, and a significant visual appearance variation
-of the same vehicle instance in different camera views. In other words
-large intra-instance differences of the same vehicle in different cameras,
-and subtle inter-instance differences between different vehicles in the same
-view, considering thousands of vehicles in a large scale smart city setting is
-the main challenge of vehicle re-ID. Moreover, unlike person re-id
-orientation of vehicles results in self occlusion and drastic visual geometry
-changes where in person re-id visual geometry or texture of the person's
-appearance (wear) will not change.
+% Our motivation
+
+% Our contributions
+In this work, we propose a noval mutual learning based network architecture,
+that aims to simultaneously learn a number of tasks, plus a consensus, to build an
+improved representation for the purpose of vehicle re-identification.
+
+These two contributions of our work are highlighted as follows:
+(1)
+(2)
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Generally, vehicle re-id task can be regarded as a fine-grained recognition task.
+%As a unique ID of a vehicle instance, license plate has been widely used for vehicle re-ID.
+%However, license plate recognition is quite sensitive to image quality,
+%camera view and occlusion. Furthermore, license plate may be removed,
+%altered even faked in some cases, making it unreliable to identify a vehicle
+%simply by its license plate. Therefore, vehicle re-ID by visual appearance is
+%of great practical value in real-world applications such as smart cities.
+
+%Another related problem to vehicle re-identification is fine-grained vehicle model
+%classification such as ``Audi A4 2014'' \cite{yang2015compcars}.
+%However, the granularity of vehicle re-identification task is much finer
+%since the ideal target is to search a specific vehicle rather than a model, in
+%which the image instances of the same vehicle (identity) forms a separate class.
+%%%% Vehicle re-id challenges
+%However,
+%vehicle re-id by visual appearance is a
+%challenging task due to the very similar appearance of different vehicle instances
+%of the same model type and color, and a significant visual appearance variation
+%of the same vehicle instance in different camera views. In other words
+%large intra-instance differences of the same vehicle in different cameras,
+%and subtle inter-instance differences between different vehicles in the same
+%view, considering thousands of vehicles in a large scale smart city setting is
+%the main challenge of vehicle re-ID. Moreover, unlike person re-id
+%orientation of vehicles results in self occlusion and drastic visual geometry
+%changes where in person re-id visual geometry or texture of the person's
+%appearance (wear) will not change.
 % re-ID problem. A human body is usually upright, thus the texture or color of
@@
 % recognition and search than Automatic Number Plate Recognition (ANPR).
-
 % be found as an instance-level object search problem.
 
-%%% matching probe gallery
-Formally re-ID  aims to find
-target images of the same identity in a large gallery set given a probe image.
-In order to match appearances of objects, firstly we need to obtain an
-embedding for the objects. A
-match is then performed by using a suitable distance metric expressing the
-closeness of two objects in an embedding space. A good embedding should be
-invariant to illumination, scale and viewpoint changes.
+%%%% matching probe gallery
+%Formally re-ID  aims to find
+%target images of the same identity in a large gallery set given a probe image.
+%In order to match appearances of objects, firstly we need to obtain an
+%embedding for the objects. A
+%match is then performed by using a suitable distance metric expressing the
+%closeness of two objects in an embedding space. A good embedding should be
+%invariant to illumination, scale and viewpoint changes.
 
-%%% we use CNNs
-Recently, Convolutional Neural Network (CNN) has achieved state-of-the-art
-performance in various computer vision
-recognition tasks, such as large-scale image classification
-face recognition  and person re-ID.
-With the supervision of a carefully designed objective loss, typically
-cross-entropy and/or triplet loss
-% contrastive loss or triplet loss
-CNN can learn efficient feature embedding
+%%%% we use CNNs
+%Recently, Convolutional Neural Network (CNN) has achieved state-of-the-art
+%performance in various computer vision
+%recognition tasks, such as large-scale image classification
+%face recognition  and person re-ID.
+%With the supervision of a carefully designed objective loss, typically
+%cross-entropy and/or triplet loss
+%% contrastive loss or triplet loss
+%CNN can learn efficient feature embedding
 
-%%% Datasets and SOTA
-Influenced by the recent advancements on person re-id vehicle re-id has started
-to gain increasing attention,
-and a number of vehicle databases and additional labeling are now available to
-facilitate this research
- including
- VeRi-776\cite{Liu2016icme-veri, Liu2016eccv_veri},
- VehicleID\cite{liu2016vehicleid} and VRIC\cite{kanaci2018vehicle} and methods
- specific to vehicle re-ID becoming more frequent in various venues
- \cite{wang2017orientation, Shen_2017_ICCV, Zhou2018VAMI}.
-
-%%% Our method:
-\todo{Expand near submission}
-In this paper we propose a new mutual learning based network architecture, that
-aims to simultaneously learn a number of tasks, plus a consensus, to build an
-improved representation for the purpose of vehicle re-identification.
-% Second, we propose to leverage multi-task learning to gen- erate discriminative
-% feature representation by the joint op- timization of group sensitive triplet
-% loss and softmax loss, which can be well applied to accomplish large scale
-% vehicle re-identification towards real applications.
+%%%% Datasets and SOTA
+%Influenced by the recent advancements on person re-id vehicle re-id has started
+%to gain increasing attention,
+%and a number of vehicle databases and additional labeling are now available to
+%facilitate this research
+% including
+% VeRi-776\cite{Liu2016icme-veri, Liu2016eccv_veri},
+% VehicleID\cite{liu2016vehicleid} and VRIC\cite{kanaci2018vehicle} and methods
+% specific to vehicle re-ID becoming more frequent in various venues
+% \cite{wang2017orientation, Shen_2017_ICCV, Zhou2018VAMI}.
+%
+%%%% Our method:
+%\todo{Expand near submission}
+%In this paper we propose a new mutual learning based network architecture, that
+%aims to simultaneously learn a number of tasks, plus a consensus, to build an
+%improved representation for the purpose of vehicle re-identification.
+%% Second, we propose to leverage multi-task learning to gen- erate discriminative
+%% feature representation by the joint op- timization of group sensitive triplet
+%% loss and softmax loss, which can be well applied to accomplish large scale
+%% vehicle re-identification towards real applications.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 classification
-\cite{liao2015exploiting,gu2013car,lin2014jointly,yang2015compcars,sochor2016boxcars,hu2017deep}.
+\cite{liao2015exploiting,yang2015compcars,sochor2016boxcars,hu2017deep}.
 But, the two problems are usually studied independently.
@@
 \noindent {\bf Vehicle Re-Identification. }
-Whist vehicle re-id is less studied than person re-id
-\cite{gong2014person,li2014deepreid,ahmed2015improved,xiao2016learning,li2017person,sun2017svdnet,Li2018Harmonious,zhong2017camera},
-there are a handful of existing methods.
+%Whist vehicle re-id is less studied than person re-id
+%\cite{gong2014person,li2018harmonious,zhong2017camera},
+%there are a handful of existing methods.
 %Notably, Feris \etal \cite{feris2012large} proposed an attribute-based re-id method.
@@
 %complex multi-step based approach, suffering from weak discriminative model generalisation.
-
 Recently, deep learning techniques have been exploited to vehicle re-id.  Liu
@@
 
-In order to perform Re-ID of previously unseen query vehicles, the aim of our model is to learn a feature embedding that allows for accurate retrivals based on distance (\eg L1) from the query image representation.
+In order to perform re-ID of previously unseen query vehicles, the aim of our model is to learn a feature embedding that allows for accurate retrivals based on distance (\eg L1) from the query image representation.
 In order to perform this task, we utilise training data containing a number of different labels: identity class labels as well as vehicle orientation class labels.
@@
 
-In order to perform accurate re-ID, we use this data to build a model constructed from a number of branches, each of which is tasked with learning a specific aspect of the data concurrently.
+In order to perform accurate re-ID, we use this data to build a model constructed from multiple branches, each of which is tasked with learning a specific aspect of the data concurrently.
 The branches of the model are as follows: A) Identity classification B) Identity classification from a scaled image C) Identity from grayscale image D) Identity plus the vehicles' orienations.
-The individual branches then form a consensus prediction on the identity of the training examples, and this consensus is then employed for regulation of the individual branches.
+These individual branches then form a consensus prediction on the identity of the training examples, and this consensus is then employed for regulation of the individual branches.
 
@@
 
-The root branch of our model is tasked with learning the best representation for vehicle identity discrimination, for both training sets.
+The root branch of our model is tasked with learning the best representation for vehicle identity discrimination, for both training sets $\mathcal{I}_1$ and $\mathcal{I}_2$.
 Here, we exploit the cross entropy classification loss function in order to train one branch to predict vehicle identity.
@@
 \begin{equation}
-  l_{ID} = -\frac{1}{N_B} \sum_{i=1}^{N_B} \log{p_i^{ID}}
+  L_{ID} = -\frac{1}{N_B} \sum_{i=1}^{N_B} \log{p_i^{ID}}
   \label{E:cross_entropy_loss}
@@
 \begin{equation}
-  l_{O} = -\frac{1}{N_B} \sum_{i=1}^{N_B}\log{p_i^{ID}} + \frac{1}{N_S} \sum_{i=1}^{N_B}q_i^O
+  L_{O} = -\frac{1}{N_B} \sum_{i=1}^{N_B}\log{p_i^{ID}} + \frac{1}{N_S} \sum_{i=1}^{N_B}q_i^O
 \end{equation}
@@
 \]
-
 %% \paragraph{(E) Vehicle Landmark Localisation}
@@
 \begin{equation}
-  l_{C} = \frac{1}{N_B} \sum_{i=1}^{N_B} \mathcal{H}_i
+  L_{C} = \frac{1}{N_B} \sum_{i=1}^{N_B} \mathcal{H}_i
 \end{equation}
@@
 
-\subsection{Re-ranking}
-
-\emph{TODO}
+%\subsection{Re-ranking}
+%\emph{TODO}
 
@@
     MTCRO \cite{xu2018framework} & 61.6 & 87.2 & 94.2 \\
-    MTCRO (ReRank) \cite{xu2018framework} & 62.6 & 88.0 & \bf{94.6} \\
+    MTCRO (ReRank) \cite{xu2018framework} & 62.6 & 88.0 & 94.6 \\
     \hline
@@
     MTML-O & 60.8 & 90.2 & 95.4 \\
-    MTML-G \emph{TODO} & 62.8 & 90.9 & 96.2 \\
+    MTML-G & 62.8 & 91.1 & 95.8 \\
     \hdashline

### 2019-05-07 paper.tex
Add Jimmy's changes plus a few of my results.

@@
 \usepackage{multirow}
-\usepackage{arydshln}
+% \usepackage{arydshln}
 \usepackage{subcaption}
@@
 \begin{abstract}
-
+Vehicle re-identification (Re-ID) aims to search a specific vehicle
+instance across non-overlapping camera views.
+%
+The main challenge of vehicle Re-ID is that
+the visual appearance of vehicles may drastically changes
+according to diverse viewpoints and illumination.
+%
+Most of existing vehicle Re-ID model cannot make full use of
+various complementary vehicle information, like vehicle identification and orientation.
+%
+In this paper, we propose a novel {\em Multi-Task Mutual Learning} (MTML) deep model
+to learn discriminative feature simultaeously from multiple branches.
+%
+Specially, we design a consensus learning loss function by fusing feature of the final convolutional feature maps from all branches.
+%
+Extensive comparative evaluations demonstrate the effectiveness of the
+proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the two existing benchmarks
+(VehicleID and VeRi-776).
+We also get a competitive result on NVIDIA 2019 AI City Challenge Track 2.
 \end{abstract}
@@
 
-%% Background of vehicle re-ID
+%% Background of vehicle Re-ID
 With the development of autonomous driving
-and smart city applications the need for accurately analyzing vehicles in these
+and smart city applications, the need for accurately analyzing vehicles in these
 scenarios with related computer vision tasks \ie detection, classification and
@@
 %
-Specially, vehicle re-identification (re-ID) attracted increasing attentions in community
-\cite{liu2016vehicleid,Liu2016cvpr_drdl,liu2016veri,Liu2016eccv_veri,
+Specially, vehicle re-identification attracted increasing attentions in community
+\cite{liu2016vehicleid,liu2016veri,liu2016veri,
 wang2017orientation,Wang_2017_ICCV,Zhou2018VAMI},
@@
 
-%% What's vehicle re-ID?
-Vehicle re-identification task aims at searching a specific vehicle
+%% What's vehicle Re-ID?
+Vehicle re-identification (Re-ID) aims at searching a specific vehicle
 instance across non-overlapping camera views.
@@
 Due to the unavailability of license plate under some circumstances,
-vehicle re-ID by visual appearance is of great practical value in real-world applications such as smart cities.
+vehicle Re-ID by visual appearance is of great practical value in real-world applications such as smart cities.
 %
 This task is similar with a more popular task: person re-identification
-\cite{gong2014re,chen2017person,Li2018Harmonious,xiao2016learning,
+\cite{gong2014re,chen2018person,Li2018Harmonious,xiao2016learning,
 li2017person,wei2018person,song2018mask,chang2018multi,
@@
 but with more challenges:
-%% Vehicle re-ID challenges
-(1) Unlike person re-id, pose/orientation of vehicles results in self occlusion and drastic visual geometry changes, since vehicle is a kind of rigid body.
+%% Vehicle Re-ID challenges
+(1) Unlike person Re-ID, pose/orientation of vehicles results in occlusion and drastic visual geometry changes, since vehicle is a kind of rigid body.
 % The same vehicle under different viewpoints are visually more diverse than person,
@@
 (2) Even the same orientation, the different identity vehicles may look very similar
-due to the similar even same vehicle model. This requires the vehicle re-id model
+due to the similar even same vehicle model. This requires vehicle Re-ID models
 to have a more powerful fine-grained recognition ability.
@@
 % Existing work's problem
+Most of vehicle Re-ID methods \cite{liu2016vehicleid,liu2016veri,Shen_2017_ICCV,Zhou2018VAMI}
+focus on using a single branch
+to learn an embedding feature for vehicle instance re-identification
+from the original information (e.g. the original whole vehicle image)
+%
+Due to the previously metioned challenges for vehicle re-identification,
+this single branch structure can not take advantage of the diversity of vehicles.
+%
+On the other hand, most existing work
+\cite{liu2016vehicleid,liu2016veri}
+train vehicle Re-ID deep learning model
+by using a single supervisory signal (like vehicle ID).
+%
+However, vehicle ID label can not reflect the two kind of differences between vehicle instances:
+(1) the vehicles with the same ID under different viewpoints,
+(2) the vehicles with the different IDs under the same viewpoints.
+Therefore, combining multiple supervisory signals (e.g. vehicle ID and vehicle orientation) together can be effective for vehicle Re-ID model learning.
 
-% Our motivation
+\begin{figure}
+%  \includegraphics[width=\linewidth,trim=0cm 8cm 0cm 0cm,clip=true]{images/system_overview_orient_only.pdf}
+  \caption{A comparision of the same vehicle ID and different ID.}
+	\label{F:veh_comparison}
+\end{figure}
 
 % Our contributions
-In this work, we propose a noval mutual learning based network architecture,
-that aims to simultaneously learn a number of tasks, plus a consensus, to build an
-improved representation for the purpose of vehicle re-identification.
+In this work, we propose a novel {\em Multi-Task Mutual Learning}
+(MTML) based network architecture,
+that aims to simultaneously learn a number of tasks from supervisory signals, plus a consensus loss function, to build an improved representation for the purpose of vehicle re-identification.
 
 These two contributions of our work are highlighted as follows:
-(1)
-(2)
+(1) we formulate a novel {\em Multi-Task Mutual Learning} (MTML) deep learning model by building an individual branch for each task for vehicle Re-ID.
+A multi-branch structure is designed for learning different tasks, such as vehicle ID, multi-scale, grayscale, and orientation.
+It aims to discover and capture concurrently complementary discriminative information.
+(2) We introduce a mutual learning mechanism for improving multi-label learning robustness.
+It makes our learning model can benefit from multiple supervisory signals, and then learn the discrimative features for vehicle Re-ID.
+%(3) we propose a cross-dataset joint learning framework for vehicle Re-ID.
+Extensive comparative evaluations demonstrate the effectiveness of the
+proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the two existing benchmarks
+(VehicleID \cite{liu2016vehicleid} and VeRi-776 \cite{liu2016veri}).
+We also get a competitive result on CityFlow \cite{tang2019cityflow} benchmark at NVIDIA 2019 AI City Challenge.
+
+\begin{figure*}[t]
+  \begin{subfigure}{.6\textwidth}
+    \includegraphics[width=\linewidth,trim=5cm 11cm 5cm 11cm,clip=true]{images/veri_orients.pdf}
+  \end{subfigure}
+  \begin{subfigure}{.4\textwidth}
+    \centering
+    \begin{tabular}{c | c | c}
+      \hline
+      Index & Orientation & Colour \\
+      \hline
+      0 & front & \textcolor{red}{red} \\
+      1 & rear & - \\
+      2 & left  & - \\
+      3 & left front & \textcolor{cyan}{cyan}  \\
+      4 & left rear & \textcolor{yellow}{yellow}  \\
+      5 & right  & - \\
+      6 & right front & \textcolor{green}{green} \\
+      7 & right rear & \textcolor{black}{black} \\
+      \hline
+    \end{tabular}
+  \end{subfigure}
+  \caption{Examples from the VeRi776 dataset with the orientation labels provided in \cite{wang2017orientation} (best viewed in colour).}
+  \label{T:veri_veh_orientations}
+\end{figure*}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Generally, vehicle re-id task can be regarded as a fine-grained recognition task.
-%As a unique ID of a vehicle instance, license plate has been widely used for vehicle re-ID.
+%Generally, vehicle Re-ID task can be regarded as a fine-grained recognition task.
+%As a unique ID of a vehicle instance, license plate has been widely used for vehicle Re-ID.
 %However, license plate recognition is quite sensitive to image quality,
@@
 %altered even faked in some cases, making it unreliable to identify a vehicle
-%simply by its license plate. Therefore, vehicle re-ID by visual appearance is
+%simply by its license plate. Therefore, vehicle Re-ID by visual appearance is
 %of great practical value in real-world applications such as smart cities.
@@
 %which the image instances of the same vehicle (identity) forms a separate class.
-%%%% Vehicle re-id challenges
+%%%% Vehicle Re-ID challenges
 %However,
-%vehicle re-id by visual appearance is a
+%vehicle Re-ID by visual appearance is a
 %challenging task due to the very similar appearance of different vehicle instances
@@
 %view, considering thousands of vehicles in a large scale smart city setting is
-%the main challenge of vehicle re-ID. Moreover, unlike person re-id
+%the main challenge of vehicle Re-ID. Moreover, unlike person Re-ID
 %orientation of vehicles results in self occlusion and drastic visual geometry
-%changes where in person re-id visual geometry or texture of the person's
+%changes where in person Re-ID visual geometry or texture of the person's
 %appearance (wear) will not change.
-% re-ID problem. A human body is usually upright, thus the texture or color of
+% Re-ID problem. A human body is usually upright, thus the texture or color of
 % his/her wear will not change severely in different views. Deploying the
-% person re-ID methods for vehicles directly cannot obtain satisfactory
+% person Re-ID methods for vehicles directly cannot obtain satisfactory
 % performance.
@@
 %%%% matching probe gallery
-%Formally re-ID  aims to find
+%Formally Re-ID  aims to find
 %target images of the same identity in a large gallery set given a probe image.
@@
 %recognition tasks, such as large-scale image classification
-%face recognition  and person re-ID.
+%face recognition  and person Re-ID.
 %With the supervision of a carefully designed objective loss, typically
@@
 %%%% Datasets and SOTA
-%Influenced by the recent advancements on person re-id vehicle re-id has started
+%Influenced by the recent advancements on person Re-ID vehicle Re-ID has started
 %to gain increasing attention,
@@
 % including
-% VeRi-776\cite{Liu2016icme-veri, Liu2016eccv_veri},
+% VeRi-776\cite{Liu2016icme-veri, liu2016veri},
 % VehicleID\cite{liu2016vehicleid} and VRIC\cite{kanaci2018vehicle} and methods
-% specific to vehicle re-ID becoming more frequent in various venues
+% specific to vehicle Re-ID becoming more frequent in various venues
 % \cite{wang2017orientation, Shen_2017_ICCV, Zhou2018VAMI}.
@@
 \noindent {\bf Vehicle Re-Identification. }
-%Whist vehicle re-id is less studied than person re-id
+%Whist vehicle Re-ID is less studied than person Re-ID
 %\cite{gong2014person,li2018harmonious,zhong2017camera},
 %there are a handful of existing methods.
-%Notably, Feris \etal \cite{feris2012large} proposed an attribute-based re-id method.
-%The vehicles are firstly classified by different attributes like car model types and colours. The re-id matching is then conducted in the attribute space.
+%Notably, Feris \etal \cite{feris2012large} proposed an attribute-based Re-ID method.
+%The vehicles are firstly classified by different attributes like car model types and colours. The Re-ID matching is then conducted in the attribute space.
 %%
@@
 %complex multi-step based approach, suffering from weak discriminative model generalisation.
-Recently, deep learning techniques have been exploited to vehicle re-id.  Liu
-\etal \cite{Liu2016eccv_veri} explored a deep neural network to estimate the
+Recently, deep learning techniques have been exploited to vehicle Re-ID.  Liu
+\etal \cite{liu2016veri} explored a deep neural network to estimate the
 visual similarities between vehicle images.
@@
 %
-Liu \etal \cite{Liu2016cvpr_drdl} also designed a Coupled Clusters Loss (CCL)
-to boost a multi-branch CNN model for vehicle re-id.
+Liu \etal \cite{liu2016vehicleid} also designed a Coupled Clusters Loss (CCL)
+to boost a multi-branch CNN model for vehicle Re-ID.
 %
@@
 \cite{Wang_2017_ICCV} considered 20 vehicle keypoints for learning and aligning
-local regions of a vehicle for re-id.  Clearly, this approach comes with extra
+local regions of a vehicle for Re-ID.  Clearly, this approach comes with extra
 cost of exhaustively labeling these keypoints in a large number of vehicle
@@
 Additionally,
-space-time contextual knowledge has also been exploited for vehicle re-id
-subject to structured scenes \cite{Liu2016eccv_veri,Shen_2017_ICCV}.
-Liu \etal \cite{Liu2016eccv_veri} proposed
+space-time contextual knowledge has also been exploited for vehicle Re-ID
+subject to structured scenes \cite{liu2016veri,Shen_2017_ICCV}.
+Liu \etal \cite{liu2016veri} proposed
 a spatio-temporal affinity approach for quantifying every pair of images.
@@
 incorporated spatio-temporal path information of vehicles.
-Whilst this method improves the re-id performance on the VeRi-776 dataset,
+Whilst this method improves the Re-ID performance on the VeRi-776 dataset,
 it may not generalize to complex scene structures when the number of
@@
 
+\noindent{\bf Multi-Task Learning. }
+Multi-task learning (MTL) is a machine learning strategy
+that learns several related tasks simultaneously for
+their mutual benefits \cite{argyriou2007multi}. %  \cite{evgeniou2004regularized,ando2005framework,argyriou2007multi}.
+A good MTL survey with focus on neural networks
+is provided in \cite{caruana1997multitask}.
+%
+Deep CNNs are well suited for
+performing MTL as they are inherently designed to learn joint
+feature representations subject to multiple label objectives
+concurrently in multi-branch architectures.
+%
+Joint learning of multiple related tasks
+has been proven to be effective in solving computer vision problems
+\cite{dong2017multi,zhang2016learning}.
+% \cite{dong2017multi,zhang2016learning,ahmed2008training}.
+%
+Critically, our method is uniquely designed to
+explore the potential of MTL
+in combining multiple diversities (e.g. scale and color) of the vechile image
+and being supervised by multiple kinds of manual labels (e.g. ID and orientation).
+Each of them is associated with an individual branch of learning model.
+
 \section{Multi-modal Vehicle Re-identification}
-\begin{figure*}
-  \begin{subfigure}{.6\textwidth}
-    \includegraphics[width=\linewidth,trim=5cm 11cm 5cm 11cm,clip=true]{images/veri_orients.pdf}
-  \end{subfigure}
-  \begin{subfigure}{.4\textwidth}
-    \centering
-    \begin{tabular}{c | c | c}
-      \hline
-      Index & Orientation & Colour \\
-      \hline
-      0 & front & \textcolor{red}{red} \\
-      1 & rear & - \\
-      2 & left  & - \\
-      3 & left front & \textcolor{cyan}{cyan}  \\
-      4 & left rear & \textcolor{yellow}{yellow}  \\
-      5 & right  & - \\
-      6 & right front & \textcolor{green}{green} \\
-      7 & right rear & \textcolor{black}{black} \\
-      \hline
-    \end{tabular}
-  \end{subfigure}
-  \caption{Examples from the VeRi776 dataset with the orientation labels provided in \cite{wang2017orientation} (best viewed in colour).}
-  \label{T:veri_veh_orientations}
-\end{figure*}
 
-In order to perform re-ID of previously unseen query vehicles, the aim of our model is to learn a feature embedding that allows for accurate retrivals based on distance (\eg L1) from the query image representation.
+In order to perform Re-ID of previously unseen query vehicles, the aim of our model is to learn a feature embedding that allows for accurate retrivals based on distance (\eg L1) from the query image representation.
 In order to perform this task, we utilise training data containing a number of different labels: identity class labels as well as vehicle orientation class labels.
@@
 
-In order to perform accurate re-ID, we use this data to build a model constructed from multiple branches, each of which is tasked with learning a specific aspect of the data concurrently.
+In order to perform accurate Re-ID, we use this data to build a model constructed from multiple branches, each of which is tasked with learning a specific aspect of the data concurrently.
 The branches of the model are as follows: A) Identity classification B) Identity classification from a scaled image C) Identity from grayscale image D) Identity plus the vehicles' orienations.
@@
 \subsection{Model Structure and Feature Learning}
+
+\begin{figure*}
+  \includegraphics[width=\linewidth,trim=0cm 8cm 0cm 0cm,clip=true]{images/system_overview_orient_only.pdf}
+  \caption{An overview of our proposed model (best viewed in colour). (A) Vehicle identity branch (B) Multi-scale analysis branch (C) Grayscale analysis branch (D) Vehicle orientation branch
+    %(E) Vehicle landmark localisation branch.
+(E) Consensus learning through feature fusion.
+Feedforward signals shown in black.
+Hard target (groundtruth) loss propagation shown in \textcolor{red}{red}.
+Soft target consensus feedback loss propagation shown in \textcolor{green}{green}.}
+  \label{F:overview}
+\end{figure*}
 
@@
 \end{equation}
-
-\begin{figure*}
-  \includegraphics[width=\linewidth,trim=0cm 8cm 0cm 0cm,clip=true]{images/system_overview_orient_only.pdf}
-  \caption{An overview of our proposed model (best viewed in colour). (A) Vehicle identity branch (B) Multi-scale analysis branch (C) Grayscale analysis branch (D) Vehicle orientation branch
-    %(E) Vehicle landmark localisation branch.
-(E) Consensus learning through feature fusion.
-Feedforward signals shown in black.
-Hard target (groundtruth) loss propagation shown in \textcolor{red}{red}.
-Soft target consensus feedback loss propagation shown in \textcolor{green}{green}.}
-  \label{F:overview}
-\end{figure*}
 
@@
 
-In order to harness the benefit of all branches for the purpose of vehicle re-identification, we employ consensus learning as proposed in \cite{chen2017person} and previously harnessed for vehicle re-id in \cite{kanaci2018vehicle}.
+In order to harness the benefit of all branches for the purpose of vehicle re-identification, we employ consensus learning as proposed in \cite{chen2017person} and previously harnessed for vehicle Re-ID in \cite{kanaci2018vehicle}.
 This is done via feature fusion of the final convolutional feature maps from all branches for consensus learning.
@@
 
+\begin{table*}
+  \centering
+  \begin{tabular}{c || c | c | c || c | c || c | c}
+    \hline
+    \multirow{2}{*}{Dataset} & \multicolumn{3}{c||}{Training} & \multicolumn{2}{c||}{Probe} & \multicolumn{2}{c}{Gallery} \\
+    \cline{2-8}
+    & \#IDs& \#Imgs & \#Orients & \#IDs & \#Imgs & \#IDs & \#Imgs \\
+    \hline
+    VeRi-776 \cite{liu2016veri}
+    & 576 & 30188 & 8 & 200 & 1678 & 200 & 11579 \\
+    VehicleID \cite{liu2016vehicleid}
+    & 13164 & 100182 & - & 2400 & 17638 & 2400 & 2400 \\
+%    BoxCars \cite{} & 21250 & 63750 & -  & - & - & - & - \\
+%    CompCars \cite{} & 1118 & 31148 & - & - & - & - & - \\
+    AICity2019 \cite{} & \\
+    \hline
+  \end{tabular}
+  \caption{Details of the datasets employed for train and test.}
+  \label{T:dataset_details}
+\end{table*}
+
 \section{Experiments}
-
 We conduct a number of experiments to explore the performance of our method.
@@
 As our method includes a branch that predicts vehicle orientation in addition to identity, our model requires data that contains the orientation labels for training.
-As a result, we include the VeRI776 dataset \cite{liu2016veri} in the training set for all our experiments.
+As a result, we include the VeRI776 \cite{liu2016veri} dataset in the training set for all our experiments.
+
+\subsection{Datasets}
+We employ a number of previously released Vehicle Re-ID datasets in our experiments, in order to train and test our method extensively.
+Firstly we conduct experiments on two benchmark datasets in Table \ref{T:dataset_details}:
+VeRi776 \cite{liu2016veri} and VehicleID \cite{liu2016vehicleid}.
+%
+The VeRi-776 dataset \cite{liu2016veri} has 37,778 images of 576 IDs in training set and 200
+IDs in test set. The standard probe and gallery sets consist of 1,678 and 11,579
+images, respectively. The data split statistics are summarised in Table 3.
+%
+The VehicleID \cite{liu2016vehicleid} dataset provides a training set with 113,346 from 13,164 IDs and a test set
+with 19,777 images from 2,400 identities. It adopts the single-shot re-id setting,
+with only one true matching for each probe. Following the standard setting, we
+repeated 10 times of randomly selected probe and gallery sets in our experiments.
 
 \subsection{Implementation Details}
-
 We employ the ResNet50 \cite{} network architecture as the base of our model.
@@
 at ranks $\leq k$.
-The mAP is calculated as the mean over all query images of the Average Precision, which itself is calculated as the precision cut-off at each correct recalled image position averaged over all possible correct gallery images \cite{}.
+The mAP is calculated as the mean over all query images of the Average Precision, which itself is calculated as the precision cut-off at each correct recalled image position averaged over all possible correct gallery images.
 
-\subsection{Vehicle Re-identification Datasets}
+\subsection{Evaluation on Veri776 Dataset}
+We train and test only the VeRi776 dataset, for comparison with previous state-of-the-art methods.
+Table \ref{T:benchmark_results_veri} shows the results of the first experiment, where we train and test only on the VeRi776 dataset.
+All experiments we continued for 150 epochs of training.
+As can be seen, even before re-ranking, our full model achieves state-of-the-art mAP and Rank-1 scores on this dataset, of 64.6\% and 92.3\% respectively.
+And after re-ranking the mAP score is increased to an impressive 68.3\%.
+%\textcolor{red}{TODO more detailed discussion of results}
 
-We employ a number of previously released Vehicle Re-ID datasets in our experiments, in order to train and test our method extensively.
-Firstly we conduct experiments on two benchmark datasets: VeRi776 and VehicleID.
-Firstly we train and test only the VeRi776 dataset, for comparison with previous state-of-the-art methods.
-And secondly we train on both the VeRi776 and VehicleID datasets, and then test on the VehicleID, for all three testsets: small, medium and large.
+\subsection{Evaluation on VehicleID Dataset}
+We train on both the VeRi776 and VehicleID datasets, and then test on the VehicleID, for all three testsets: small, medium and large.
 We conduct the latter experiment in this was due to the fact that our method requires some training data with orientation labels.
@@
 
-\begin{table*}
-  \centering
-  \begin{tabular}{c || c | c | c || c | c || c | c}
-    \hline
-    \multirow{2}{*}{Dataset} & \multicolumn{3}{c||}{Training} & \multicolumn{2}{c||}{Probe} & \multicolumn{2}{c}{Gallery} \\
-    \cline{2-7}
-    & \#IDs& \#Imgs & \#Orients & \#IDs & \#Imgs & \#IDs & \#Imgs \\
-    \hline
-    VeRi-776 \cite{} & 576 & 30188 & 8 & 200 & 1678 & 200 & 11579 \\
-    VehicleID \cite{} & 13164 & 100182 & - & 2400 & 17638 & 2400 & 2400 \\
-    BoxCars \cite{} & 21250 & 63750 & -  & - & - & - & - \\
-    CompCars \cite{} & 1118 & 31148 & - & - & - & - & - \\
-    AICity2019 \cite{} & \\
-    \hline
-  \end{tabular}
-  \caption{Details of the datasets employed for train and test.}
-  \label{T:dataset_details}
-\end{table*}
-
-Table \ref{T:benchmark_results_veri} shows the results of the first experiment, where we train and test only on the VeRi776 dataset.
-All experiments we continued for 150 epochs of training.
-As can be seen, even before re-ranking, our full model achieves state-of-the-art mAP and Rank-1 scores on this dataset, of 64.6 and 92.3 respectively.
-And after re-ranking the mAP score is increased to an impressive 68.3.
-
-\emph{TODO more detailed discussion of results}
+\textcolor{red}
+{
+Table \ref{T:benchmark_results_vehicleid} shows that ...
+(Please add some comparison methods in Table 3)
+}
 
@@
     MTML-G & 62.8 & 91.1 & 95.8 \\
-    \hdashline
+    \hline
     MTML-SG & 63.7 & 90.6 & 95.8 \\
@@
     MTML-OSG & \bf{64.6} & \bf{92.3} & 95.7 \\
-    \hdashline
     MTML-OSG (ReRank) & \bf{\emph{68.3}} & 92.0 & 94.2 \\
@@
 
-\begin{table*}
+\begin{table}
   \centering
+  \setlength{\tabcolsep}{0.01cm}
   \begin{tabular}{l || c | c || c | c || c | c }
@@
   \label{T:benchmark_results_vehicleid}
-\end{table*}
+\end{table}
 
 \subsection{NVIDIA AI City Challenge 2019}
+
+\begin{table}[ht]
+  \centering
+  \begin{tabular}{l || c | c | c }
+    \hline
+    Method & mAP & Rank-1 & Rank-5 \\
+    \hline
+    MSVF \cite{kanaci2018vehicle} & & & \\
+    MTCRO (ReRank) \cite{xu2018framework} &  & & \\
+    \hline
+    MTML-S &  & & \\
+    MTML-G & 19.7 & 44.6 & 58.5 \\
+    \hline
+    MTML-SG & 20.6 & 44.2 & 55.8 \\
+    \hline
+    MTML-SG (ReRank) &  & & \\
+    \hline
+  \end{tabular}
+  \caption{Trained/tested on CityFlow}
+  \label{T:cityflow_results}
+\end{table}
+
+\begin{table}[ht]
+  \centering
+  \setlength{\tabcolsep}{0.01cm}
+  \begin{tabular}{l|c|c|c|c|c|c}
+  \hline
+  \multicolumn{1}{r|}{Test:} & \multicolumn{3}{c|}{VeRi-776} & \multicolumn{3}{c}{CityFlow} \\
+  \hline
+  Method       & mAP    & Rank-1   & Rank-5   & mAP    & Rank-1   & Rank-5   \\
+  \hline
+  MTML-S       &        &          &          &        &          &          \\
+  MTML-O       &        &          &          &        &          &          \\
+  MTML-G       &        &          &          &        &          &          \\
+  MTML-SG      &        &          &          &        &          &          \\
+  MTML-OG      &        &          &          &        &          &          \\
+  MTML-OSG     &        &          &          &        &          &      \\
+  \hline
+  \end{tabular}
+  \caption{Trained/tested on CityFlow+VeRi-776}
+  \label{T:cf_veri_res}
+\end{table}
 
@@
 
-\begin{table}
-  \centering
-  \begin{tabular}{l || c | c}
-
-  \end{tabular}
-  \caption{}
-  \label{T:aicity_results}
-\end{table}
-
-\subsection{Analysis}
+%\begin{table}
+%  \centering
+%  \begin{tabular}{l || c | c}
+%
+%  \end{tabular}
+%  \caption{}
+%  \label{T:aicity_results}
+%\end{table}
 
 \section{Conclusions}
+Due to the main challenge of vehicle Re-ID: the visual appearance of vehicles may drastically changes
+according to diverse viewpoints and illumination.
+%
+In this paper, we propose a novel {\em Multi-Task Mutual Learning} (MTML) deep model
+to learn discriminative feature simultaeously from multiple branches.
+%
+Specially, we design a consensus learning loss function by fusing feature of the final convolutional feature maps from all branches.
+%
+Extensive comparative evaluations demonstrate the effectiveness of the
+proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the two existing benchmarks
+(VehicleID and VeRi-776).
+We also get a competitive result on NVIDIA 2019 AI City Challenge Track 2.
 
@@
 \bibliographystyle{cvpr2019AuthorKit/latex/ieee_fullname}
-\bibliography{bibliography.bib}
+\bibliography{bibliography}
 }

### 2019-05-08 paper.tex
Add Aytac and Sean's changes.

@@
 Most of existing vehicle Re-ID model cannot make full use of
-various complementary vehicle information, like vehicle identification and orientation.
+various complementary vehicle information, e.g. vehicle type and orientation.
 %
@@
 (VehicleID and VeRi-776).
-We also get a competitive result on NVIDIA 2019 AI City Challenge Track 2.
+We also yield competitive performance on the NVIDIA 2019 AI City Challenge Track 2.
 \end{abstract}
@@
 With the development of autonomous driving
-and smart city applications, the need for accurately analyzing vehicles in these
-scenarios with related computer vision tasks \ie detection, classification and
+and smart city applications, the need for accurately analyzing vehicles on urban streets 
+by incorporating all the necessary computer vision tasks including detection, classification and
 pose estimation as well as re-identification is ever-increasing.
 %
-Specially, vehicle re-identification attracted increasing attentions in community
+Specially, vehicle re-identification attracted increasing attentions in the research community
 \cite{liu2016vehicleid,liu2016veri,liu2016veri,
@@
 since it can play an important role in
-intelligent transportation system and social safety.
+intelligent transportation systems and public safety.
 
@@
 %
-Due to the unavailability of license plate under some circumstances,
+Due to the unavailability of license plate under uncontrolled view angles,
 vehicle Re-ID by visual appearance is of great practical value in real-world applications such as smart cities.
@@
 % The same vehicle under different viewpoints are visually more diverse than person,
-This means that the same identity must be inferred with any pose/orientation of the vehicle is given.
-(2) Even the same orientation, the different identity vehicles may look very similar
-due to the similar even same vehicle model. This requires vehicle Re-ID models
-to have a more powerful fine-grained recognition ability.
+This means that the same identity must be inferred with any given pose/orientation of a vehicle.
+(2) Even in the same orientation, vehicles of different identities may look very similar
+due to the same vehicle model. This requires vehicle Re-ID models
+to have a more discriminative fine-grained recognition ability.
 
@@
 to learn an embedding feature for vehicle instance re-identification
-from the original information (e.g. the original whole vehicle image)
+from the original information (e.g. the original whole vehicle image).
 %
@@
 %
-On the other hand, most existing work
+Moreover, most existing works
 \cite{liu2016vehicleid,liu2016veri}
 train vehicle Re-ID deep learning model
-by using a single supervisory signal (like vehicle ID).
+using a single supervisory signal (e.g. vehicle ID).
 %
-However, vehicle ID label can not reflect the two kind of differences between vehicle instances:
-(1) the vehicles with the same ID under different viewpoints,
-(2) the vehicles with the different IDs under the same viewpoints.
-Therefore, combining multiple supervisory signals (e.g. vehicle ID and vehicle orientation) together can be effective for vehicle Re-ID model learning.
+However, vehicle ID label {\em alone} can not differentiate the differences between vehicles due to:
+(1) vehicle instances of the same ID under different viewpoints,
+(2) vehicle instances of different IDs under the same viewpoint.
+We suggest that imposing multiple and different supervisory signals
+simultaneously (e.g. vehicle ID and vehicle orientation) is more effective
+for learning more fine-grained discriminative features for vehicle
+Re-ID.
 
-\begin{figure}
-%  \includegraphics[width=\linewidth,trim=0cm 8cm 0cm 0cm,clip=true]{images/system_overview_orient_only.pdf}
-  \caption{A comparision of the same vehicle ID and different ID.}
-	\label{F:veh_comparison}
-\end{figure}
+%\begin{figure}
+%%  \includegraphics[width=\linewidth,trim=0cm 8cm 0cm 0cm,clip=true]{images/system_overview_orient_only.pdf}
+%  \caption{A comparision of the same vehicle ID and different ID.}
+%	\label{F:veh_comparison}
+%\end{figure}
 
@@
 (MTML) based network architecture,
-that aims to simultaneously learn a number of tasks from supervisory signals, plus a consensus loss function, to build an improved representation for the purpose of vehicle re-identification.
+that aims to simultaneously learn a number of recognition tasks from
+different supervisory signals, plus a consensus loss function, to
+build an improved representation for the purpose of vehicle
+re-identification.
 
-These two contributions of our work are highlighted as follows:
-(1) we formulate a novel {\em Multi-Task Mutual Learning} (MTML) deep learning model by building an individual branch for each task for vehicle Re-ID.
-A multi-branch structure is designed for learning different tasks, such as vehicle ID, multi-scale, grayscale, and orientation.
-It aims to discover and capture concurrently complementary discriminative information.
-(2) We introduce a mutual learning mechanism for improving multi-label learning robustness.
-It makes our learning model can benefit from multiple supervisory signals, and then learn the discrimative features for vehicle Re-ID.
+We make two contributions in this work as follows:
+(1) We formulate a novel {\em Multi-Task Mutual Learning} (MTML) deep
+learning model by building each individual branch for a different
+recognition task relevant to vehicle Re-ID and by taking into
+consideration different four tasks including vehicle ID, multi-scale, grayscale, and orientation.
+Our model aims to discover and capture concurrently complementary discriminative information.
+(2) We introduce a mutual learning mechanism for improving multi-task learning robustness.
+Our model benefits from multiple supervisory signals in order to
+enhance model learning of more discrimative features for vehicle Re-ID.
 %(3) we propose a cross-dataset joint learning framework for vehicle Re-ID.
@@
 (VehicleID \cite{liu2016vehicleid} and VeRi-776 \cite{liu2016veri}).
-We also get a competitive result on CityFlow \cite{tang2019cityflow} benchmark at NVIDIA 2019 AI City Challenge.
+We also yield competitive performance on the CityFlow
+\cite{tang2019cityflow} benchmark at the NVIDIA 2019 AI City Challenge.
 
@@
 \cite{liao2015exploiting,yang2015compcars,sochor2016boxcars,hu2017deep}.
-But, the two problems are usually studied independently.
+The two problems are usually studied independently.
 For example, Yang et al. \cite{yang2015compcars} propose a part attributes driven
@@
 selecting spatial salient vehicle parts in order to learn more
-discriminative model representations without explicit parts annotations, with
+discriminative model representations without explicit parts annotations.
 
@@
 %complex multi-step based approach, suffering from weak discriminative model generalisation.
-Recently, deep learning techniques have been exploited to vehicle Re-ID.  Liu
+Deep learning techniques have been exploited to vehicle Re-ID. For instance, Liu
 \etal \cite{liu2016veri} explored a deep neural network to estimate the
@@
 %
-To explore local information and motivated by the idea of landmark alignment
+To explore local information motivated by the idea of landmark alignment
 \cite{zhang2014facial} in both face recognition \cite{taigman2014deepface} and
@@
 images, and the implicit assumption of having sufficient image
-resolution/details for computing these keypoints.
+resolution/details for extracting these keypoints.
 %
@@
 and being supervised by multiple kinds of manual labels (e.g. ID and orientation).
-Each of them is associated with an individual branch of learning model.
+Each of them is associated with an individual branch of a single model.
 
@@
 
-An overview of our proposed model can be seen in Figure \ref{F:overview}.
-The model is composed of a number of sub-branches, each of which is simultaneously learning a representation to solve its own set of tasks.
-In addition, there is a single fusion branch, which allows feature selection to be performed from the entire collection of individual representations.
-It is the output from this branch that is taken during deployment.
-Each sub-branch will now be described in more detail.
+An overview of our proposed model can be seen in Figure
+\ref{F:overview}. The model is composed of four sub-branches, each of
+which is simultaneously learning a representation to solve its own
+task. In addition, there is a single fusion branch, which allows
+feature selection to be performed from the entire collection of
+individual representations. It is the output from this branch that is
+taken during deployment. Each sub-branch will now be described in more
+detail.
 
@@
 
-In order to encourage the model to focus on details of the vehicles, that allow for separation of highly similar identity classes, we ensure that one branch will be unable to use colour information for distinguishing between these classes.
-This is simply done by giving as input only the grayscale image, and again training the branch to predict identity via the cross entropy loss.
+In order to encourage the model to focus on details of the vehicles,
+that allow for separation of highly similar identity classes, we
+ensure that one branch will be unable to use colour information for
+distinguishing between these classes. This is done by giving as input
+only the grayscale image, and again training the branch to predict
+identity via the cross entropy loss.
 
@@
 
-This branch is tasked with learning a representation to simultaneously predict the identity class and the orientation class, for examples for which this is known.
+This branch is tasked with learning a representation to simultaneously
+predict the identity class and the orientation class when this is known.
 %In the case where the training images do not have associated orientation labels, this branch is trained in exactly the same way as the Vehicle Identity branch outlined above.
@@
     VeRi-776 \cite{liu2016veri}
-    & 576 & 30188 & 8 & 200 & 1678 & 200 & 11579 \\
-    VehicleID \cite{liu2016vehicleid}
-    & 13164 & 100182 & - & 2400 & 17638 & 2400 & 2400 \\
+    & 576 & 37778 & 8 & 200 & 1678 & 200 & 11579 \\
+%     VehicleID \cite{liu2016vehicleid}
+%     & 13164 & 100182 & - & 2400 & 17638 & 2400 & 2400 \\
 %    BoxCars \cite{} & 21250 & 63750 & -  & - & - & - & - \\
 %    CompCars \cite{} & 1118 & 31148 & - & - & - & - & - \\
-    AICity2019 \cite{} & \\
+    CityFlow \cite{tang2019cityflow} 
+    & 333 & 36935 & - & 333 & 1052 & 333 & 18290 \\
     \hline
@@
 \section{Experiments}
-We conduct a number of experiments to explore the performance of our method.
-First we exploit a number of widely available vehicle ID benchmark datasets in order to assess the benefit of each of the branches of our model independently, and altogether.
-Then we compare the performance of our model to other current work by looking at our performance in the NVIDIA AI City Challenge 2019 Task 2 (Vehicle Re-identification).
-As our method includes a branch that predicts vehicle orientation in addition to identity, our model requires data that contains the orientation labels for training.
-As a result, we include the VeRI776 \cite{liu2016veri} dataset in the training set for all our experiments.
 
-\subsection{Datasets}
-We employ a number of previously released Vehicle Re-ID datasets in our experiments, in order to train and test our method extensively.
-Firstly we conduct experiments on two benchmark datasets in Table \ref{T:dataset_details}:
-VeRi776 \cite{liu2016veri} and VehicleID \cite{liu2016vehicleid}.
-%
-The VeRi-776 dataset \cite{liu2016veri} has 37,778 images of 576 IDs in training set and 200
-IDs in test set. The standard probe and gallery sets consist of 1,678 and 11,579
-images, respectively. The data split statistics are summarised in Table 3.
-%
-The VehicleID \cite{liu2016vehicleid} dataset provides a training set with 113,346 from 13,164 IDs and a test set
-with 19,777 images from 2,400 identities. It adopts the single-shot re-id setting,
-with only one true matching for each probe. Following the standard setting, we
-repeated 10 times of randomly selected probe and gallery sets in our experiments.
-
-\subsection{Implementation Details}
-We employ the ResNet50 \cite{} network architecture as the base of our model.
-We train the model with minibatches of size 8, using the Adam optimisation technique with a learning rate of 0.0001, exponential decay rates set as follows: $\beta_1=0.9$ and $\beta_2=0.999$.
-The two image sizes used were standard $224\x224$ and small (for the scaled branch) $160\x160$.
-
-We measure the performance of our vehicle re-identification methods according to the standard Cumulative Matching Characteristic (CMC) and mean Average Precision (mAP).
-The CMC is computed on each individual rank $k$ as the cumulative percentage of correct matches appearing
-at ranks $\leq k$.
-The mAP is calculated as the mean over all query images of the Average Precision, which itself is calculated as the precision cut-off at each correct recalled image position averaged over all possible correct gallery images.
-
-\subsection{Evaluation on Veri776 Dataset}
-We train and test only the VeRi776 dataset, for comparison with previous state-of-the-art methods.
-Table \ref{T:benchmark_results_veri} shows the results of the first experiment, where we train and test only on the VeRi776 dataset.
-All experiments we continued for 150 epochs of training.
-As can be seen, even before re-ranking, our full model achieves state-of-the-art mAP and Rank-1 scores on this dataset, of 64.6\% and 92.3\% respectively.
-And after re-ranking the mAP score is increased to an impressive 68.3\%.
-%\textcolor{red}{TODO more detailed discussion of results}
-
-\subsection{Evaluation on VehicleID Dataset}
-We train on both the VeRi776 and VehicleID datasets, and then test on the VehicleID, for all three testsets: small, medium and large.
-We conduct the latter experiment in this was due to the fact that our method requires some training data with orientation labels.
-As VeRi776 is the only dataset with labels of this kind, we must therefore include it in the training.
-
-\textcolor{red}
-{
-Table \ref{T:benchmark_results_vehicleid} shows that ...
-(Please add some comparison methods in Table 3)
-}
-
-\begin{table}
+\begin{table}[h]
   \centering
@@
 
-\begin{table}
-  \centering
-  \setlength{\tabcolsep}{0.01cm}
-  \begin{tabular}{l || c | c || c | c || c | c }
-    \hline
-    \multirow{2}{*}{Method} & \multicolumn{2}{c}{Small} & \multicolumn{2}{c}{Medium} &\multicolumn{2}{c}{Large} \\
-    \cline{2-7}
-    & mAP & Rank-1 & mAP & Rank-1 & mAP & Rank-1 \\
-    \hline
-    MTML-S & \\
-    MTML-O & \\
-    MTML-G & \\
-    % \hdashline
-    MTML-SG & \\
-    MTML-OG & \\
-    MTML-OSG & \\
-    % \hdashline
-    MTML-OSG+ReRank & \\
-    \hline
-  \end{tabular}
-  \caption{Trained on VeRi776+VehicleID, tested on VehicleID}
-  \label{T:benchmark_results_vehicleid}
-\end{table}
+We conduct a number of experiments to explore the performance of our method.
+First we exploit a number of widely available vehicle ID benchmark datasets in order to assess the benefit of each of the branches of our model independently, and altogether.
+Then we compare the performance of our model to other current work by looking at our performance in the NVIDIA AI City Challenge 2019 Task 2 (Vehicle Re-identification).
+As our method includes a branch that predicts vehicle orientation in addition to identity, our model requires data that contains the orientation labels for training.
+As a result, we include the VeRI776 \cite{liu2016veri} dataset in the training set for all our experiments.
+
+\subsection{Datasets}
+We employ a number of previously released Vehicle Re-ID datasets in our experiments, in order to train and test our method extensively.
+Firstly we conduct experiments on two benchmark datasets in Table \ref{T:dataset_details}:
+VeRi776 \cite{liu2016veri} and VehicleID \cite{liu2016vehicleid}.
+%
+The VeRi-776 dataset \cite{liu2016veri} has 37,778 images of 576 IDs in training set and 200
+IDs in test set. The standard probe and gallery sets consist of 1,678 and 11,579
+images, respectively. The data split statistics are summarised in Table 3.
+%
+The VehicleID \cite{liu2016vehicleid} dataset provides a training set with 113,346 from 13,164 IDs and a test set
+with 19,777 images from 2,400 identities. It adopts the single-shot re-id setting,
+with only one true matching for each probe. Following the standard setting, we
+repeated 10 times of randomly selected probe and gallery sets in our experiments.
+
+\subsection{Implementation Details}
+We employ the ResNet50 \cite{} ({\bf SG: missing reference}) network
+architecture as the base of our model. We train the model with
+minibatches of size 8, using the Adam optimisation technique with a
+learning rate of 0.0001, exponential decay rates set as follows:
+$\beta_1=0.9$ and $\beta_2=0.999$. The two image sizes used were
+standard $224\x224$ and small (for the scaled branch) $160\x160$.
+
+We measure the performance of our vehicle re-identification methods according to the standard Cumulative Matching Characteristic (CMC) and mean Average Precision (mAP).
+The CMC is computed on each individual rank $k$ as the cumulative percentage of correct matches appearing
+at ranks $\leq k$.
+The mAP is calculated as the mean over all query images of the Average Precision, which itself is calculated as the precision cut-off at each correct recalled image position averaged over all possible correct gallery images.
+
+\subsection{Evaluation on the Veri776 Dataset}
+First, we train and test on the VeRi776 dataset so to compare with
+existing state-of-the-art methods on identical settings.
+Table \ref{T:benchmark_results_veri} shows the results of the first
+experiment, where we train and test only on the VeRi776 dataset. All
+experiments we continued for 150 epochs of training. As can be seen,
+even before re-ranking, our full model achieves state-of-the-art mAP
+and Rank-1 scores on this dataset, of 64.6\% and 92.3\%
+respectively. And after re-ranking the mAP score is increased to an
+impressive 68.3\%. 
+%\textcolor{red}{TODO more detailed discussion of results}
+
+\subsection{Evaluation on the VehicleID Dataset}
+Second, we then train on both the VeRi776 and VehicleID datasets, and
+test on VehicleID with all three of its test sets: small, medium and
+large. We conducted this experiment to explore the benefit of training
+model using additional orientation labels, as VeRi776 is the only
+dataset available with orientation labels.
+
+\textcolor{red}
+{
+Table \ref{T:benchmark_results_vehicleid} shows that ...
+(Please add some comparison methods in Table 3)
+}
+({\bf SG: missing results})
+
+%\begin{table}
+%  \centering
+%  \setlength{\tabcolsep}{0.01cm}
+%  \begin{tabular}{l || c | c || c | c || c | c }
+%    \hline
+%    \multirow{2}{*}{Method} & \multicolumn{2}{c}{Small} & \multicolumn{2}{c}{Medium} &\multicolumn{2}{c}{Large} \\
+%    \cline{2-7}
+%    & mAP & Rank-1 & mAP & Rank-1 & mAP & Rank-1 \\
+%    \hline
+%    MTML-S & \\
+%    MTML-O & \\
+%    MTML-G & \\
+%    % \hdashline
+%    MTML-SG & \\
+%    MTML-OG & \\
+%    MTML-OSG & \\
+%    % \hdashline
+%    MTML-OSG+ReRank & \\
+%    \hline
+%  \end{tabular}
+%  \caption{Trained on VeRi776+VehicleID, tested on VehicleID}
+%  \label{T:benchmark_results_vehicleid}
+%\end{table}
 
@@
 
-\begin{table}[ht]
+\begin{table}[h]
   \centering
@@
     \hline
-    MSVF \cite{kanaci2018vehicle} & & & \\
-    MTCRO (ReRank) \cite{xu2018framework} &  & & \\
+    Resnet50\cite{tang2019cityflow} & 25.5 & 41.3 & - \\
     \hline
-    MTML-S &  & & \\
-    MTML-G & 19.7 & 44.6 & 58.5 \\
-    \hline
-    MTML-SG & 20.6 & 44.2 & 55.8 \\
-    \hline
+    MTML-S  & 17.0 & 40.4 & 53.3 \\
+    MTML-G  & 19.6 & 44.5 & 58.4 \\
+    \hdashline
+    MTML-SG & 20.6 & 44.1 & 55.8 \\
+    \hdashline
     MTML-SG (ReRank) &  & & \\
@@
 
-\begin{table}[ht]
+\begin{table}[h]
   \centering
-  \setlength{\tabcolsep}{0.01cm}
+  \setlength{\tabcolsep}{0.05cm}
   \begin{tabular}{l|c|c|c|c|c|c}
@@
   \hline
+  MTML-O       &       &         &         &       &        &         \\
   MTML-S       &       &         &         &       &        &         \\
-  MTML-O       &        &          &          &        &          &          \\
-  MTML-G       &        &          &          &        &          &          \\
-  MTML-SG      &        &          &          &        &          &          \\
+  MTML-G       & 61.6  & 89.7    & 95.1    &       &        &         \\
+  MTML-SG      & 62.6  & 90.8    & 95.8    &       &        &         \\
   MTML-OG      &       &         &         &       &        &         \\
@@
 \section{Conclusions}
-Due to the main challenge of vehicle Re-ID: the visual appearance of vehicles may drastically changes
-according to diverse viewpoints and illumination.
+Vehicle Re-ID is difficult because the visual appearance of
+a vehicle instance may drastically change due to diverse
+viewpoints and illumination, whilst different vehicle instances of the same
+model type may have a very similar appearance.
 %
@@
 %
-Specially, we design a consensus learning loss function by fusing feature of the final convolutional feature maps from all branches.
+Moreover, we design a consensus learning loss function by fusing feature of the final convolutional feature maps from all branches.
 %
@@
 (VehicleID and VeRi-776).
-We also get a competitive result on NVIDIA 2019 AI City Challenge Track 2.
+We also yield a competitive performance on the NVIDIA 2019 AI City Challenge Track 2.
 

### 2019-05-08 paper.tex
Minor corrections to intro and related work sections, plus add a few more citations. Also strengthen the argument in the intro.

@@
 In this paper, we propose a novel {\em Multi-Task Mutual Learning} (MTML) deep model
-to learn discriminative feature simultaeously from multiple branches.
+to learn discriminative features simultaeously from multiple branches.
 %
-Specially, we design a consensus learning loss function by fusing feature of the final convolutional feature maps from all branches.
+Specially, we design a consensus learning loss function by fusing features from the final convolutional feature maps from all branches.
 %
-Extensive comparative evaluations demonstrate the effectiveness of the
+Extensive comparative evaluations demonstrate the effectiveness of our
 proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the two existing benchmarks
@@
 With the development of autonomous driving
-and smart city applications, the need for accurately analyzing vehicles on urban streets 
-by incorporating all the necessary computer vision tasks including detection, classification and
-pose estimation as well as re-identification is ever-increasing.
+and smart city applications, the need to accurately analyze vehicles on urban streets
+via multiple computer vision tasks such as detection, classification and
+pose estimation, as well as re-identification, is ever-increasing.
 %
-Specially, vehicle re-identification attracted increasing attentions in the research community
+Specially, vehicle re-identification has attracted increasing attention in the research community
 \cite{liu2016vehicleid,liu2016veri,liu2016veri,
 wang2017orientation,Wang_2017_ICCV,Zhou2018VAMI},
-since it can play an important role in
+as it can play an important role in
 intelligent transportation systems and public safety.
@@
 %% What's vehicle Re-ID?
-Vehicle re-identification (Re-ID) aims at searching a specific vehicle
+Vehicle re-identification (Re-ID) aims to search a specific vehicle
 instance across non-overlapping camera views.
 %
-Due to the unavailability of license plate under uncontrolled view angles,
-vehicle Re-ID by visual appearance is of great practical value in real-world applications such as smart cities.
+Due to the fact that the license plate is often not visible in a number of view angles (which are generally uncontrolled),
+vehicle Re-ID by visual appearance alone is of great practical value in real-world applications such as smart cities.
 %
-This task is similar with a more popular task: person re-identification
+This task is similar to a more popular task: person re-identification
 \cite{gong2014re,chen2018person,Li2018Harmonious,xiao2016learning,
@@
 %% Vehicle Re-ID challenges
-(1) Unlike person Re-ID, pose/orientation of vehicles results in occlusion and drastic visual geometry changes, since vehicle is a kind of rigid body.
+(1) Unlike person Re-ID, the pose/orientation of vehicles results in occlusion and drastic visual geometry changes, since the vehicle is a kind of rigid body.
 % The same vehicle under different viewpoints are visually more diverse than person,
-This means that the same identity must be inferred with any given pose/orientation of a vehicle.
+This means that is difficult to infer the same identity from any given pose/orientation of a vehicle.
 (2) Even in the same orientation, vehicles of different identities may look very similar
-due to the same vehicle model. This requires vehicle Re-ID models
+due to the being of the same, or similar, vehicle model. This requires vehicle Re-ID models
 to have a more discriminative fine-grained recognition ability.
@@
 % Existing work's problem
-Most of vehicle Re-ID methods \cite{liu2016vehicleid,liu2016veri,Shen_2017_ICCV,Zhou2018VAMI}
-focus on using a single branch
-to learn an embedding feature for vehicle instance re-identification
+Most previously proposed vehicle Re-ID methods \cite{liu2016vehicleid,liu2016veri,Shen_2017_ICCV,Zhou2018VAMI} focus on using a single branch
+to learn an embedded feature representation for vehicle instance re-identification
 from the original information (e.g. the original whole vehicle image).
 %
-Due to the previously metioned challenges for vehicle re-identification,
+Due to the previously mentioned challenges for vehicle re-identification,
 this single branch structure can not take advantage of the diversity of vehicles.
@@
 \cite{liu2016vehicleid,liu2016veri}
-train vehicle Re-ID deep learning model
+train their vehicle Re-ID deep learning model
 using a single supervisory signal (e.g. vehicle ID).
 %
-However, vehicle ID label {\em alone} can not differentiate the differences between vehicles due to:
-(1) vehicle instances of the same ID under different viewpoints,
-(2) vehicle instances of different IDs under the same viewpoint.
-We suggest that imposing multiple and different supervisory signals
-simultaneously (e.g. vehicle ID and vehicle orientation) is more effective
-for learning more fine-grained discriminative features for vehicle
-Re-ID.
+However, we argue that vehicle ID label {\em alone} can not differentiate the differences between vehicles due to the issues we raised above.
+But additionally we can make use of the fact that the orientation of a vehicle alters its view in a predictable manner.
+As a result, we suggest that imposing multiple and different supervisory signals
+simultaneously - the vehicle ID \emph{and} vehicle orientation - allows the model to learn this variation in a more well-defined manner, and is thus more effective
+for learning the fine-grained discriminative features necessary for vehicle
+Re-ID. As orientation labels were provided by Wang \etal \cite{Wang_2017_ICCV} for the VeRi dataset \cite{liu2016veri}, is is possible to make use of these multiple signals for this purpose.
 
@@
 recognition task relevant to vehicle Re-ID and by taking into
-consideration different four tasks including vehicle ID, multi-scale, grayscale, and orientation.
-Our model aims to discover and capture concurrently complementary discriminative information.
+consideration four different tasks: vehicle ID, multi-scale, grayscale, and orientation.
+Our model aims to discover and capture concurrently the complementary discriminative information.
 (2) We introduce a mutual learning mechanism for improving multi-task learning robustness.
@@
 %complex multi-step based approach, suffering from weak discriminative model generalisation.
-Deep learning techniques have been exploited to vehicle Re-ID. For instance, Liu
+A number of deep learning techniques have been exploited for the purpose vehicle Re-ID. For instance, Liu
 \etal \cite{liu2016veri} explored a deep neural network to estimate the
@@
 local regions of a vehicle for Re-ID.  Clearly, this approach comes with extra
-cost of exhaustively labeling these keypoints in a large number of vehicle
+cost of exhaustively labelling these keypoints in a large number of vehicle
 images, and the implicit assumption of having sufficient image
@@
 explore the potential of MTL
-in combining multiple diversities (e.g. scale and color) of the vechile image
-and being supervised by multiple kinds of manual labels (e.g. ID and orientation).
-Each of them is associated with an individual branch of a single model.
+in combining multiple diversities (e.g. scale and color) of the vehicle image
+and being supervised by multiple kinds of manual labels (e.g. ID and orientation) with each of them being associated with an individual branch of a single model.
 
@@
 This is done via feature fusion of the final convolutional feature maps from all branches for consensus learning.
-As our branches are based on the ResNet50 architecture, these feature maps are formed via an average pooling operation which result in feature vectors of length $2048$.
+As our branches are based on the ResNet50 architecture \cite{he2016deep}, these feature maps are formed via an average pooling operation which result in feature vectors of length $2048$.
 Hence our fused features are of length $8192$.
@@
 Additionally, we also utilise a consensus propagation mechanism, similar to the previously proposed method \cite{chen2017person,kanaci2018vehicle}.
-Here the consensus output is taken as 'soft targets' (as opposed to the groundtruth label 'hard targets') for the training data, and used to feedback information about the predictions made by the entire ensemble of branches.
+Here the consensus output is taken as `soft targets' (as opposed to the groundtruth label `hard targets') for the training data, and used to feedback information about the predictions made by the entire ensemble of branches.
 This is done concurrently with the training of the individual branches.
@@
 \subsection{Implementation Details}
-We employ the ResNet50 \cite{} ({\bf SG: missing reference}) network
+We employ the ResNet50 \cite{he2016deep} network
 architecture as the base of our model. We train the model with
@@
 
-\textcolor{red}
-{
-Table \ref{T:benchmark_results_vehicleid} shows that ...
-(Please add some comparison methods in Table 3)
-}
-({\bf SG: missing results})
+%% \textcolor{red}
+%% {
+%% Table \ref{T:benchmark_results_vehicleid} shows that ...
+%% (Please add some comparison methods in Table 3)
+%% }
+%% ({\bf SG: missing results})
 

### 2019-05-08 paper.tex
Add some discussion of results in the experiments sections and remove references to VehicleID dataset. Plus add references to the orientation labels and move figs around a bit.

@@
 for learning the fine-grained discriminative features necessary for vehicle
-Re-ID. As orientation labels were provided by Wang \etal \cite{Wang_2017_ICCV} for the VeRi dataset \cite{liu2016veri}, is is possible to make use of these multiple signals for this purpose.
+Re-ID.
+As orientation labels were provided by Wang \etal \cite{Wang_2017_ICCV} for the VeRi dataset \cite{liu2016veri}, is is possible to make use of these multiple signals for this purpose.
+Examples of the orientation labels provided by this paper can be seen in Figure \ref{F:veri_veh_orientations}.
+
+\begin{figure*}[t]
+  \begin{subfigure}{.6\textwidth}
+    \includegraphics[width=\linewidth,trim=5cm 11cm 5cm 11cm,clip=true]{images/veri_orients.pdf}
+  \end{subfigure}
+  \begin{subfigure}{.4\textwidth}
+    \centering
+    \begin{tabular}{c | c | c}
+      \hline
+      Index & Orientation & Colour \\
+      \hline
+      0 & front & \textcolor{red}{red} \\
+      1 & rear & - \\
+      2 & left  & - \\
+      3 & left front & \textcolor{cyan}{cyan}  \\
+      4 & left rear & \textcolor{yellow}{yellow}  \\
+      5 & right  & - \\
+      6 & right front & \textcolor{green}{green} \\
+      7 & right rear & \textcolor{black}{black} \\
+      \hline
+    \end{tabular}
+  \end{subfigure}
+  \caption{Examples from the VeRi776 dataset with the orientation labels provided in \cite{wang2017orientation} (best viewed in colour).}
+  \label{F:veri_veh_orientations}
+\end{figure*}
 
@@
 \cite{tang2019cityflow} benchmark at the NVIDIA 2019 AI City Challenge.
-
-\begin{figure*}[t]
-  \begin{subfigure}{.6\textwidth}
-    \includegraphics[width=\linewidth,trim=5cm 11cm 5cm 11cm,clip=true]{images/veri_orients.pdf}
-  \end{subfigure}
-  \begin{subfigure}{.4\textwidth}
-    \centering
-    \begin{tabular}{c | c | c}
-      \hline
-      Index & Orientation & Colour \\
-      \hline
-      0 & front & \textcolor{red}{red} \\
-      1 & rear & - \\
-      2 & left  & - \\
-      3 & left front & \textcolor{cyan}{cyan}  \\
-      4 & left rear & \textcolor{yellow}{yellow}  \\
-      5 & right  & - \\
-      6 & right front & \textcolor{green}{green} \\
-      7 & right rear & \textcolor{black}{black} \\
-      \hline
-    \end{tabular}
-  \end{subfigure}
-  \caption{Examples from the VeRi776 dataset with the orientation labels provided in \cite{wang2017orientation} (best viewed in colour).}
-  \label{T:veri_veh_orientations}
-\end{figure*}
 
@@
 \subsection{Datasets}
-We employ a number of previously released Vehicle Re-ID datasets in our experiments, in order to train and test our method extensively.
-Firstly we conduct experiments on two benchmark datasets in Table \ref{T:dataset_details}:
-VeRi776 \cite{liu2016veri} and VehicleID \cite{liu2016vehicleid}.
+We employ two Vehicle Re-ID datasets in our experiments, in order to train and test our method extensively.
+Firstly we conduct experiments on a benchmark dataset, VeRi776 \cite{liu2016veri}, which has been widely tested by the majority of recent works.
+And secondly we employ the new CityFlow dataset \cite{tang2019cityflow}, a challenging dataset that has been shown to be more difficult than previous publicly available benchmarks.
 %
-The VeRi-776 dataset \cite{liu2016veri} has 37,778 images of 576 IDs in training set and 200
-IDs in test set. The standard probe and gallery sets consist of 1,678 and 11,579
-images, respectively. The data split statistics are summarised in Table 3.
+The VeRi-776 dataset \cite{liu2016veri} has 37,778 images of 576 IDs in the training set and 200
+IDs in the test set. The standard probe and gallery sets consist of 1,678 and 11,579
+images, respectively. There are also orientation labels, for 8 possible orientations, available for the VeRi-776 dataset, which were provided by \cite{Wang_2017_ICCV}.
 %
-The VehicleID \cite{liu2016vehicleid} dataset provides a training set with 113,346 from 13,164 IDs and a test set
-with 19,777 images from 2,400 identities. It adopts the single-shot re-id setting,
-with only one true matching for each probe. Following the standard setting, we
-repeated 10 times of randomly selected probe and gallery sets in our experiments.
+%% The VehicleID \cite{liu2016vehicleid} dataset provides a training set with 113,346 from 13,164 IDs and a test set
+%% with 19,777 images from 2,400 identities. It adopts the single-shot re-id setting,
+%% with only one true matching for each probe. Following the standard setting, we
+%% repeated 10 times of randomly selected probe and gallery sets in our experiments.
+%
+The CityFlow dataset \cite{tang2019cityflow} has 36,935 images of 333 IDs in the training set and 333 different IDs in the test set.
+The standard probe and gallery sets consist of 1,052 and 18,290 images respectively.
+The data split statistics of both datasets are summarised in Table \ref{T:dataset_details}.
 
@@
 \subsection{Evaluation on the Veri776 Dataset}
-First, we train and test on the VeRi776 dataset so to compare with
-existing state-of-the-art methods on identical settings.
-Table \ref{T:benchmark_results_veri} shows the results of the first
-experiment, where we train and test only on the VeRi776 dataset. All
-experiments we continued for 150 epochs of training. As can be seen,
+Firstly, we train and test on the VeRi776 dataset in order to compare with
+existing state-of-the-art methods with identical settings.
+In order to experiment the benefit of adding each of the separate branches of our model, we take branch A (vehicle identity) as our central branch, and of course all models have an E consensus branch, and then perform experiments where we include each of the other branches in turn.
+So MTML-S refers to a model built from branches A, B and E only, MTML-G has branches A, C and E only, and so on.
+We then test versions of the model with three branches (e.g.
+MTML-SG includes branches A, B, C and E).
+MTML-OSG is then our full model, and MTML-OSG (ReRank) the results of the full model after additional re-ranking.
+Table \ref{T:benchmark_results_veri} shows the results of this
+experiment, with all experiments run for 150 epochs of training. As can be seen,
 even before re-ranking, our full model achieves state-of-the-art mAP
@@
 impressive 68.3\%.
+
+The experiments also show how the individual branches contribute to the performance, with orientation improving over the result of a scaled analysis, and grayscale doing even better.
+This demonstrates how allowing the model to learn about the orientation of the vehicle at the same time as identity can strengthen the performance.
+And that removal of the colour during learning - though obviously a useful indicator of identity at test time - allows for the model to focus on the more discriminatory features of the identity that ultimately boosts the re-id performance.
+
+The combinations of three branches all show improvement over only two, though not as well as combining all four in the MTML-OSG model.
+These results show that combining all the different tasks does indeed allow for the overall model to perform better in the final task of vehicle re-identification.
+
 %\textcolor{red}{TODO more detailed discussion of results}
 
-\subsection{Evaluation on the VehicleID Dataset}
-Second, we then train on both the VeRi776 and VehicleID datasets, and
-test on VehicleID with all three of its test sets: small, medium and
-large. We conducted this experiment to explore the benefit of training
-model using additional orientation labels, as VeRi776 is the only
-dataset available with orientation labels.
+%% \subsection{Evaluation on the VehicleID Dataset}
+%% Second, we then train on both the VeRi776 and VehicleID datasets, and
+%% test on VehicleID with all three of its test sets: small, medium and
+%% large. We conducted this experiment to explore the benefit of training
+%% model using additional orientation labels, as VeRi776 is the only
+%% dataset available with orientation labels.
 

### 2019-05-08 paper.tex
Minor changes.

@@
 
-The experiments also show how the individual branches contribute to the performance, with orientation improving over the result of a scaled analysis, and grayscale doing even better.
+The mAP results from the experiments also show how the individual branches contribute to the performance, with orientation (60.8\%) improving over the result of scaled analysis alone (59.4\%), and grayscale doing even better (62.8\%).
 This demonstrates how allowing the model to learn about the orientation of the vehicle at the same time as identity can strengthen the performance.
@@
 
-The combinations of three branches all show improvement over only two, though not as well as combining all four in the MTML-OSG model.
-These results show that combining all the different tasks does indeed allow for the overall model to perform better in the final task of vehicle re-identification.
+The combinations of three branches all show improvement over only two, with MTML-SG and MTML-OG achieving mAPs of 63.7\% and 63.5\% respectively.
+However they are still outperformed by combining all four branches in the MTML-OSG model.
+These results show that combining all the different signals for MTL does indeed allow for the overall model to perform better in the final task of vehicle re-identification.
 

### 2019-05-08 paper.tex
Add Jimmy's changes and Aytac's results.

@@
 Extensive comparative evaluations demonstrate the effectiveness of our
-proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the two existing benchmarks
-(VehicleID and VeRi-776).
+proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the a large-scale benchmarks VeRi-776.
 We also yield competitive performance on the NVIDIA 2019 AI City Challenge Track 2.
@@
 Extensive comparative evaluations demonstrate the effectiveness of the
-proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the two existing benchmarks
-(VehicleID \cite{liu2016vehicleid} and VeRi-776 \cite{liu2016veri}).
+proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the a large-scale benchmark
+%VehicleID \cite{liu2016vehicleid} and 
+VeRi-776 \cite{liu2016veri}.
 We also yield competitive performance on the CityFlow
@@
 
-\subsection{Evaluation on the Veri776 Dataset}
+\subsection{Evaluation on Veri776 Dataset}
 Firstly, we train and test on the VeRi776 dataset in order to compare with
@@
 MTML-SG includes branches A, B, C and E).
-MTML-OSG is then our full model, and MTML-OSG (ReRank) the results of the full model after additional re-ranking.
+MTML-OSG (branches A, B, C, D and E) is then our full model, and MTML-OSG (ReRank \cite{zhong2017re}) the results of the full model after additional re-ranking.
 Table \ref{T:benchmark_results_veri} shows the results of this
@@
 
-\subsection{NVIDIA AI City Challenge 2019}
+\subsection{Evaluation on CityFlow Dataset}
 
@@
     \hline
-    Resnet50\cite{tang2019cityflow} & 25.5 & 41.3 & - \\
+    Resnet50 \cite{tang2019cityflow} & 25.5 & 41.3 & - \\
     \hline
@@
   MTML-S       &       &         &         &       &        &         \\
-  MTML-G       & 61.6  & 89.7    & 95.1    &       &        &         \\
-  MTML-SG      & 62.6  & 90.8    & 95.8    &       &        &         \\
+  MTML-G       & 61.6  & 89.7    & 95.1    & 22.3  & 47.4   & 57.3   \\
+  MTML-SG      & 62.6  & 90.8    & 95.8    & 23.0  & 46.6   & 60.5   \\
   MTML-OG      &       &         &         &       &        &         \\
@@
 Multiple cameras were placed at multiple intersections and no camera information was provided about the images.
+
+Two groups of experiments are conducted on CityFlow benchmark: 
+(1) Training on CityFlow, and (2) Training on CityFlow and Veri-776.
+%
+For the first group experiment, we trained MTML-S (branch A, B and E), 
+MTML-G (branch A, C and E) and MTML-SG model only on CityFlow training data.
+Table \ref{T:cityflow_results} shows that: 
+(1) -G branch combination is much better than -S branch combination. 
+The potential reason is that grayscale analysis is more useful than mult-scale in vehicle Re-ID.
+(2) Joint learning with -S and -G is better than any individual one of them on mAP evaluation.
+
+%The reason of combine Veri-776 dataset into training set is that
+Since the orientation label is only available in Veri-776, 
+for training the full MTML model including orientation supervisory signal,
+we did the second group experiment.
+%
+%Table \ref{T:cf_veri_res} shows that:
 
@@
 Extensive comparative evaluations demonstrate the effectiveness of the
-proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the two existing benchmarks
-(VehicleID and VeRi-776).
+proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the a existing large-scale benchmarks VeRi-776.
+%VehicleID and
 We also yield a competitive performance on the NVIDIA 2019 AI City Challenge Track 2.

### 2019-05-13 paper.tex
Add final changes before submission.

@@
 \and
-Aytac Kanaci \hspace{0.7cm}
+Ayta\c{c} Kanac\i \hspace{0.7cm}
 %Queen Mary University of London\\
@@
   \end{subfigure}
-  \caption{Examples from the VeRi776 dataset with the orientation labels provided in \cite{wang2017orientation} (best viewed in colour).}
+  \caption{Examples from the VeRi-776 dataset with the orientation labels provided in \cite{wang2017orientation} (best viewed in colour).}
   \label{F:veri_veh_orientations}
@@
 During deployment, we employ the feature fusion layer from our trained model as the full feature representation in order to perform vehicle re-identification matching.
-As we do not necessarily have camera information about the query or gallery images, or timestamp information, which would allow the use of camera distance or time-based analysis, we use only a generic distance metric - the $L1$ metric - in order to match gallery images to the query.
+As we do not necessarily have camera information about the query or gallery images, or timestamp information, which would allow the use of camera distance or time-based analysis, we use only a generic distance metric - the $L2$ metric - in order to match gallery images to the query.
 Hence, for each of the query image $\mathbf{I}^q$, and the gallery images $\{\mathbf{I}_i^g\}$,  we compute our $6400$ dimension fused feature representations, $\mathbf{x}^q$ and $\{\mathbf{x}_i^g\}$ respectively.
-We then calculate the $L1$ distance between the query representation and each of the gallery images, and rank the latter by increasing distance in order to calculate the Rank-1 and mAP performance scores.
+We then calculate the $L2$ distance between the query representation and each of the gallery images, and rank the latter by increasing distance in order to calculate the Rank-1 and mAP performance scores.
 
@@
   \end{tabular}
-  \caption{Trained/tested on VeRi776 only}
+  \caption{Trained/tested on VeRi-776 only}
   \label{T:benchmark_results_veri}
@@
 We employ two Vehicle Re-ID datasets in our experiments, in order to train and test our method extensively.
-Firstly we conduct experiments on a benchmark dataset, VeRi776 \cite{liu2016veri}, which has been widely tested by the majority of recent works.
+Firstly we conduct experiments on a benchmark dataset, VeRi-776 \cite{liu2016veri}, which has been widely tested by the majority of recent works.
 And secondly we employ the new CityFlow dataset \cite{tang2019cityflow}, a challenging dataset that has been shown to be more difficult than previous publicly available benchmarks.
@@
 \subsection{Evaluation on Veri776 Dataset}
-Firstly, we train and test on the VeRi776 dataset in order to compare with
+Firstly, we train and test on the VeRi-776 dataset in order to compare with
 existing state-of-the-art methods with identical settings.
@@
 %% \subsection{Evaluation on the VehicleID Dataset}
-%% Second, we then train on both the VeRi776 and VehicleID datasets, and
+%% Second, we then train on both the VeRi-776 and VehicleID datasets, and
 %% test on VehicleID with all three of its test sets: small, medium and
 %% large. We conducted this experiment to explore the benefit of training
-%% model using additional orientation labels, as VeRi776 is the only
+%% model using additional orientation labels, as VeRi-776 is the only
 %% dataset available with orientation labels.
@@
 %  \end{tabular}
-%  \caption{Trained on VeRi776+VehicleID, tested on VehicleID}
+%  \caption{Trained on VeRi-776+VehicleID, tested on VehicleID}
 %  \label{T:benchmark_results_vehicleid}
@@
 \subsection{Evaluation on CityFlow Dataset}
+
+%%% Old %50 percent table %%%
+% \begin{table}[h]
+%   \centering
+%   \begin{tabular}{l || c | c | c }
+%     \hline
+%     Method & mAP & Rank-1 & Rank-5 \\
+%     \hline
+%     Resnet50 \cite{tang2019cityflow} & 25.5 & 41.3 & - \\
+%     \hline
+%     MTML-S  & 17.0 & 40.4 & 53.3 \\
+%     MTML-G  & 19.6 & \bf 44.5 & \bf 58.4 \\
+% %    \hdashline
+%     \hline
+%     MTML-SG & \bf{20.6} & 44.1 & 55.8 \\
+% %    \hdashline
+%     MTML-SG (ReRank) & \bf{\emph {25.7}} & 43.4 & 47.2 \\
+%     \hline
+%   \end{tabular}
+%   \caption{Trained/tested on CityFlow}
+%   \label{T:cityflow_results}
+% \end{table}
 
@@
     \hdashline
-    MTML-SG (ReRank) &  & & \\
+    MTML-SG (ReRank) & 25.7 & 43.4 & 47.2 \\
     \hline
@@
   \setlength{\tabcolsep}{0.05cm}
-  \begin{tabular}{l|c|c|c|c|c|c}
+    \begin{tabular}{p{2cm}|c|c|c|c|c|c}
   \hline
-  \multicolumn{1}{r|}{Test:} & \multicolumn{3}{c|}{VeRi-776} & \multicolumn{3}{c}{CityFlow} \\
+  \multicolumn{1}{r|}{} & \multicolumn{3}{c|}{VeRi-776} & \multicolumn{3}{c}{CityFlow} \\
   \hline
@@
   \hline
-  MTML-O       &       &         &         &       &        &         \\
-  MTML-S       &       &         &         &       &        &         \\
-  MTML-G       & 61.6  & 89.7    & 95.1    & 22.3  & 47.4   & 57.3   \\
-  MTML-SG      & 62.6  & 90.8    & 95.8    & 23.0  & 46.6   & 60.5   \\
-  MTML-OG      &       &         &         &       &        &         \\
-  MTML-OSG     &       &         &         &       &        &      \\
+% %50 percent results
+%   MTML-S       & 58.4  & 88.5    & 94.6    & 19.7  & 42.4   & 56.0    \\
+%   MTML-O       & 59.2  & 89.9    & 94.9    & 20.9  & 46.6   & 59.6    \\
+%   MTML-G       & 61.6  & 89.7    & 95.1    & 22.3  & 47.4   & 57.3   \\
+%   \hline
+%   MTML-SG      & 62.6  & 90.8    & \bf{95.8}    & 23.0  & 46.6   & 60.5   \\
+%   MLML-OG      & 62.0  & 91.2    & 95.6    & 23.8  & 49.1   & 60.9    \\
+%   MTML-OSG    & \bf{62.6}  & 90.6    & 95.5   & \bf{24.6}  & \bf{51.1}   & \bf{61.5} \\
+%   MTML-OSG (ReRank)   & \bf{\emph{66.4}}  & \bf{91.5}    & 93.6   & \bf{\emph{30.4}}  & 50.9   & 53.7 \\
+  MTML-S       & 58.4  & 88.5    & 94.6    & 18.9  & 40.6   & 53.3   \\
+  MTML-O       & 59.2  & 89.9    & 94.9    & 20.3  & 44.3   & 56.0   \\
+  MTML-G       & 61.6  & 89.7    & 95.1    & 21.6  & 46.1   & 57.5   \\
+    \hdashline
+  MTML-SG      & 62.6  & 90.8    & \bf{95.8}  & 22.1  & 45.8  & 56.5   \\
+  MLML-OG      & 62.0  & \bf{91.2}  & 95.6    & 22.9  & 46.6  & 58.2    \\
+  MTML-OSG     & \bf{62.6}  & 90.6   & 95.5   & \bf{23.6}  & \bf{48.9}  & \bf{59.7}   \\
+    \hdashline
+  MTML-OSG (ReRank)   & \bf{\emph{66.4}}  & 91.5  & 93.6  & \bf{\emph{29.2}}  & 48.8 & 50.7  \\
   \hline
@@
 
-We participated in Task 2 of the NVIDIA AI City Challenge 2019.
-The aim of this task was attempt city-scale multi-camera vehicle re-identification.
-Multiple cameras were placed at multiple intersections and no camera information was provided about the images.
+\begin{figure*}[ht]
+    \centering
+    \renewcommand{\arraystretch}{2.8}
+    \begin{tabular}{rcl}
+        & \textbf{AP} & \textbf{Query - Ranks(1-10)} \\ 
+    \multirow{2}{*}{\textbf{a)}} & 0.34        &  \multirow{2}{*}{\begin{minipage}{0.7\textwidth} \includegraphics[width=\linewidth]{images/pair_a.png} \end{minipage} }  \\
+                                 & 0.51        &                        \\
+
+    \multirow{2}{*}{\textbf{b)}} & 0.19        &  \multirow{2}{*}{\begin{minipage}{0.7\textwidth} \includegraphics[width=\linewidth]{images/pair_b.png} \end{minipage} }  \\
+                                 & 0.81        &                        \\
+
+    \multirow{2}{*}{\textbf{c)}} & 0.09        &  \multirow{2}{*}{\begin{minipage}{0.7\textwidth} \includegraphics[width=\linewidth]{images/pair_c.png} \end{minipage} }  \\
+                                 & 0.18        &                        \\
+
+    \multirow{2}{*}{\textbf{d)}} & 0.33        &  \multirow{2}{*}{\begin{minipage}{0.7\textwidth} \includegraphics[width=\linewidth]{images/pair_d.png} \end{minipage} }  \\
+                                 & 1.0         &                       
+    \end{tabular}
+    \renewcommand{\arraystretch}{1}
+%	\vspace{-0.2cm}
+
+    \caption{
+        Qulitative comparison of example query images between expriment with
+        and without orientaion branch.
+        Rank-1 to Rank-10 is shown. Each pair compares MTML-SG
+        (upper) to MTML-OSG (below) trained and tested on the VeRi-776. 
+        AP refers to Average Precision of that query. 
+    }
+    \label{fig:ranks}
+%    \vspace{-0.7cm}
+\end{figure*}
+
+We participated in Task 2 of the NVIDIA AI City Challenge 2019. The aim of this
+task was attempt city-scale multi-camera vehicle re-identification. Multiple
+cameras were placed at multiple intersections and no camera information was
+provided about the images.
 
 Two groups of experiments are conducted on CityFlow benchmark: 
-(1) Training on CityFlow, and (2) Training on CityFlow and Veri-776.
+(1) Training on CityFlow, and (2) Training on CityFlow and VeRi-776.
 %
@@
 (2) Joint learning with -S and -G is better than any individual one of them on mAP evaluation.
+Another interesting thing is that
+after re-ranking algorithm, mAP performance improves while CMC performace drops.
+The possible reason is that more similar image vehicles will get close after re-ranking.
+This means some false matching images at high rank will ``attract'' more false matching images after re-ranking.
+In such a case, it will impact CMC performance.
 
-%The reason of combine Veri-776 dataset into training set is that
-Since the orientation label is only available in Veri-776, 
+%The reason of combine VeRi-776 dataset into training set is that
+Since the orientation label is only available in VeRi-776, 
 for training the full MTML model including orientation supervisory signal,
@@
 %
-%Table \ref{T:cf_veri_res} shows that:
+Table \ref{T:cf_veri_res} shows that: 
+(1) By adding VeRi-776 training data,
+with MTML-S, MTML-G and MTML-SG, 
+we all obtain the better mAP and CMC performance on CityFlow
+than the model only training on CityFlow.
+Meanwhile, the mAP and CMC performance is a slightly lower on VeRi-776
+than the model only training on VeRi-776. We suspect this is due to training
+for 100 epochs, compared to 150.
+(2) By adding orientation branch, MLTML-OSG totaling 4 bracnhes, 
+we obtian the best mAP performance {62.6\%} and {23.6\%} on VeRi-776 and
+CityFlow repectively. 
+This shows that our mutual learning between orientation branch supervised by orientation label and other branches supervised by ID label is effective.
+
+%(1) After including Veri776 data for training orientation branch (O branch),
+%we get a better mAP performance (23.8\%) than only tr on CityFlow dataset.
+%(2) we can get the best mAP performance XXX\% and XXX\% 
+%on VeRi-776 and CityFlow respectively
+%by combining all branches of our model.
+
+Qualitative result comparison with or without orientation branch are shown in
+Figure~\ref{fig:ranks}. The advantage of learning orientation and ID signal can
+be seen in each pair where in MTML-OSG different views of the same ID vehicle
+are ranked higher compared to MTML-SG (Figure~\ref{fig:ranks}(a,b,d)). It can also be observerd that similar
+viewpoints better grouped together in the ranks (Figure~\ref{fig:ranks}(c,d)).
 

### 2019-05-16 paper.tex
A number of minor corrections to the paper.

@@
 %
-Most of existing vehicle Re-ID model cannot make full use of
+Most existing vehicle Re-ID models cannot make full use of
 various complementary vehicle information, e.g. vehicle type and orientation.
@@
 In this paper, we propose a novel {\em Multi-Task Mutual Learning} (MTML) deep model
-to learn discriminative features simultaeously from multiple branches.
+to learn discriminative features simultaneously from multiple branches.
 %
-Specially, we design a consensus learning loss function by fusing features from the final convolutional feature maps from all branches.
+Specifically, we design a consensus learning loss function by fusing features from the final convolutional feature maps from all branches.
 %
 Extensive comparative evaluations demonstrate the effectiveness of our
-proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the a large-scale benchmarks VeRi-776.
+proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on a large-scale benchmark dataset, VeRi-776.
 We also yield competitive performance on the NVIDIA 2019 AI City Challenge Track 2.
@@
 \cite{liu2016vehicleid,liu2016veri,liu2016veri,
-wang2017orientation,Wang_2017_ICCV,Zhou2018VAMI},
+wang2017orientation,wang2017orientation,Zhou2018VAMI},
 as it can play an important role in
@@
 As a result, we suggest that imposing multiple and different supervisory signals
-simultaneously - the vehicle ID \emph{and} vehicle orientation - allows the model to learn this variation in a more well-defined manner, and is thus more effective
+simultaneously (e.g. the vehicle ID \emph{and} vehicle orientation) allows the model to learn this variation in a more well-defined manner, and is thus more effective
 for learning the fine-grained discriminative features necessary for vehicle
 Re-ID.
-As orientation labels were provided by Wang \etal \cite{Wang_2017_ICCV} for the VeRi dataset \cite{liu2016veri}, is is possible to make use of these multiple signals for this purpose.
+As orientation labels were provided by Wang \etal \cite{wang2017orientation} for the VeRi dataset \cite{liu2016veri}, is is possible to make use of these multiple signals for this purpose.
 Examples of the orientation labels provided by this paper can be seen in Figure \ref{F:veri_veh_orientations}.
@@
 human body pose estimation \cite{newell2016stacked}, Wang \etal
-\cite{Wang_2017_ICCV} considered 20 vehicle keypoints for learning and aligning
+\cite{wang2017orientation} considered 20 vehicle keypoints for learning and aligning
 local regions of a vehicle for Re-ID.  Clearly, this approach comes with extra
@@
 IDs in the test set. The standard probe and gallery sets consist of 1,678 and 11,579
-images, respectively. There are also orientation labels, for 8 possible orientations, available for the VeRi-776 dataset, which were provided by \cite{Wang_2017_ICCV}.
+images, respectively. There are also orientation labels, for 8 possible orientations, available for the VeRi-776 dataset, which were provided by \cite{wang2017orientation}.
 %
@@
 existing state-of-the-art methods with identical settings.
-In order to experiment the benefit of adding each of the separate branches of our model, we take branch A (vehicle identity) as our central branch, and of course all models have an E consensus branch, and then perform experiments where we include each of the other branches in turn.
+In order to experiment the benefit of adding each of the separate branches of our model, we take branch A (vehicle identity) as our central branch, and all models have an E consensus branch.
+We then perform experiments where we include each of the other branches in turn.
 So MTML-S refers to a model built from branches A, B and E only, MTML-G has branches A, C and E only, and so on.
-We then test versions of the model with three branches (e.g.
+We then test versions of the model with three branches plus E (e.g.
 MTML-SG includes branches A, B, C and E).
 MTML-OSG (branches A, B, C, D and E) is then our full model, and MTML-OSG (ReRank \cite{zhong2017re}) the results of the full model after additional re-ranking.
-Table \ref{T:benchmark_results_veri} shows the results of this
-experiment, with all experiments run for 150 epochs of training. As can be seen,
+Table \ref{T:benchmark_results_veri} shows the results of this, with all experiments run for 150 epochs of training.
+As can be seen,
 even before re-ranking, our full model achieves state-of-the-art mAP
@@
     \caption{
-        Qulitative comparison of example query images between expriment with
-        and without orientaion branch.
+        Qualitative comparison of example query images between experiments with
+        and without inclusion of the orientaion branch.
         Rank-1 to Rank-10 is shown. Each pair compares MTML-SG
@@
 
-Two groups of experiments are conducted on CityFlow benchmark: 
+Two sets of experiments are conducted on CityFlow benchmark:
 (1) Training on CityFlow, and (2) Training on CityFlow and VeRi-776.
 %
-For the first group experiment, we trained MTML-S (branch A, B and E), 
+For the first set of experiments, we trained MTML-S (branch A, B and E),
 MTML-G (branch A, C and E) and MTML-SG model only on CityFlow training data.
 Table \ref{T:cityflow_results} shows that:
-(1) -G branch combination is much better than -S branch combination. 
+(1) MTML-G branch combination is much better than MTML-S branch combination.
 The potential reason is that grayscale analysis is more useful than mult-scale in vehicle Re-ID.
-(2) Joint learning with -S and -G is better than any individual one of them on mAP evaluation.
-Another interesting thing is that
+(2) Joint learning with MTML-SG is better than any individual one of them on mAP evaluation.
+Another interesting observation is that
 after re-ranking algorithm, mAP performance improves while CMC performace drops.
@@
 for training the full MTML model including orientation supervisory signal,
-we did the second group experiment.
+we did the second experiment which included both this database plus CityFlow.
 %
@@
 with MTML-S, MTML-G and MTML-SG,
-we all obtain the better mAP and CMC performance on CityFlow
-than the model only training on CityFlow.
+we all obtain a better mAP and CMC performance on CityFlow
+than the model which was only trained on CityFlow.
 Meanwhile, the mAP and CMC performance is a slightly lower on VeRi-776
 than the model only training on VeRi-776. We suspect this is due to training
-for 100 epochs, compared to 150.
-(2) By adding orientation branch, MLTML-OSG totaling 4 bracnhes, 
-we obtian the best mAP performance {62.6\%} and {23.6\%} on VeRi-776 and
-CityFlow repectively. 
-This shows that our mutual learning between orientation branch supervised by orientation label and other branches supervised by ID label is effective.
+for a shorter period of time, as this experiment ran for only 100 epochs, compared to 150.
+(2) By adding orientation branch, the MLTML-OSG model totalling 4 branches,
+we obtain the best mAP performance {62.6\%} and {23.6\%} on VeRi-776 and
+CityFlow respectively.
+This shows that our method of mutual learning between the orientation branch supervised by orientation labels and the other branches supervised by ID label is effective.
 
@@
 
-Qualitative result comparison with or without orientation branch are shown in
-Figure~\ref{fig:ranks}. The advantage of learning orientation and ID signal can
-be seen in each pair where in MTML-OSG different views of the same ID vehicle
-are ranked higher compared to MTML-SG (Figure~\ref{fig:ranks}(a,b,d)). It can also be observerd that similar
-viewpoints better grouped together in the ranks (Figure~\ref{fig:ranks}(c,d)).
+Qualitative results showing a comparison of rankings with or without orientation branch are shown in Figure~\ref{fig:ranks}. The advantage of learning both the orientation and ID signal can
+be seen in each pair where the MTML-OSG model is able to rank very different views of the same ID vehicle highly, which compares to the MTML-SG model which can only find images containing similar viewpoints, many of which are incorrect IDs (Figure~\ref{fig:ranks}(a,b,d)).
+It can also be observerd that similar viewpoints are better grouped together in the ranks (Figure~\ref{fig:ranks}(c,d)).
 
@@
 \section{Conclusions}
-Vehicle Re-ID is difficult because the visual appearance of
+Vehicle Re-ID is a difficult problem due to the fact that the visual appearance of
 a vehicle instance may drastically change due to diverse
@@
 
+\section{Acknowledgements}
+
 {\small

### 2019-05-16 paper.tex
More minor changes.

@@
 for a shorter period of time, as this experiment ran for only 100 epochs, compared to 150.
-(2) By adding orientation branch, the MLTML-OSG model totalling 4 branches,
+(2) By adding the orientation branch, for the MLTML-OSG model,
 we obtain the best mAP performance {62.6\%} and {23.6\%} on VeRi-776 and
-CityFlow respectively.
+CityFlow respectively. This is improved to {66.4\%} and {29.2\%} with reranking.
 This shows that our method of mutual learning between the orientation branch supervised by orientation labels and the other branches supervised by ID label is effective.

### 2019-05-16 paper.tex
Add acknowledgements and minor change.

@@
         Qualitative comparison of example query images between experiments with
-        and without inclusion of the orientaion branch.
+        and without inclusion of the orientation branch.
         Rank-1 to Rank-10 is shown. Each pair compares MTML-SG
         (upper) to MTML-OSG (below) trained and tested on the VeRi-776.
-        AP refers to Average Precision of that query.
+        AP refers to Average Precision of that query. Correct and
+        incorrect identity matches are shown with \textcolor{green}{green}
+        and \textcolor{red}{red} borders around images, respectively.
     }
@@
 
+This work is partially supported by Vision Semantics Limited and the
+Innovate UK Industrial Challenge Project on Developing and Commercialising
+Intelligent Video Analytics Solutions for Public Safety (98111-571149).
+
 {\small
